### 2023-07-30 Manuscript/Intro.tex

\usepackage{graphicx} 
\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{graphicx}
\usepackage{enumerate}
\usepackage{natbib}
\usepackage{booktabs}
\usepackage{hyperref}
\hypersetup{colorlinks = true, linkcolor = blue, citecolor=blue, urlcolor = blue}
\usepackage{enumitem}
\newcommand{\blind}{0}
\addtolength{\oddsidemargin}{-.5in}%
\addtolength{\evensidemargin}{-.5in}%
\addtolength{\textwidth}{1in}%
\addtolength{\textheight}{1.3in}%
\addtolength{\topmargin}{-.8in}%

\begin{document}

\def\spacingset#1{\renewcommand{\baselinestretch}%
{#1}\small\normalsize} \spacingset{1}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\if0\blind
{
  \title{\bf The usage of bootstrap method in shape-restricted regression}
  \author{Guanghong Yi\\
  Jun Yan\\[1ex]
  Department of Statistics, University of Connecticut\\
}
  \maketitle
} \fi

\if1\blind
{
  \bigskip
  \bigskip
  \bigskip
  \begin{center}
    {\LARGE\bf The usage of bootstrap method in shape-restricted regression}
\end{center}
  \medskip
} \fi

\bigskip
\begin{abstract}
The bootstrap method is an important resampling technique used to estimate statistics on a population by repeatedly sampling the data. It is also an effective approach for estimating the measure of dispersion in a dataset, especially in regression analysis. However, in some cases, regression models need to be constrained with known characteristics such as monotonicity or curvature, for example, in growth curves, where the coefficients are forced to be non-negative. In such situations, spline regression is used for modeling. It is not always certain whether the bootstrap method can be directly applied to estimate the dispersion under these shape-restricted scenarios, especially for pointwise confidence intervals. In this article, we will demonstrate the usage of the bootstrap method in shape-restricted regression and proof the effectiveness of bootstrap for constructing pointwise confidence intervals in shape-restricted regression empirically.
\end{abstract}

\noindent%
{\it Keywords:}  bootstrap; shape-restricted regression; pointwise confidence interval; growth curve; splines regression
\vfill

\newpage
\spacingset{1.45} 
\section{Introduction}
\label{sec:intro}

Bootstrap is a powerful and important resampling method for estimating population parameters or assessing the accuracy of a statistical procedure by repeatedly sampling the data with replacement. Its effectiveness have been widely recognized in regression analysis. By bootstrap, we can estimate the standard errors of the regression coefficients. Even for unknown underlying population distributions, bootstrap method can resample the data with replacement and computes the regression coefficients for each resampled dataset. By repeating this process many times, it provides an empirical estimate of the standard errors, which can be valuable when the assumptions of traditional standard error estimation techniques are violated. It can also be used to construct confidence intervals for regression coefficients. By resampling the dataset, bootstrap can determining the percentile intervals of these coefficients, we can obtain approximate confidence intervals for the regression parameters. Bootstrap can also construct the approximate confidence interval for certain time points f(t)s in the function by simulating f'(t) certain times in certain time points. However, when dealing with shape-restricted regressions, where the coefficients are forced to adhere to specific constraints such as monotonicity or curvature, the effectiveness of bootstrap is not proved to be guaranteed. In this paper, we will demonstrate the usage of the bootstrap method in shape-restricted regression and proof the effectiveness of bootstrap for constructing pointwise confidence intervals in shape-restricted regression empirically.

The rest of the paper is organized as the follows. Section~\ref{Bootstrap Method for Constructing Confidence Intervals} gives a review of bootstrap method for constructing confidence intervals. Section~\ref{Shape Restricted Example} gives out a shape-restricted regression example and the usage of bootstrap to build the pointwise confidence intervals for certain time points. Section~\ref{Simulation Study} shows a simulation study to assess the performance of the methods.
explores the case where a combination of the first two scenarios occurs. An  
adjusted bootstrap procedure is proposed as a working solution in this case.  
Section~\ref{Conclusion} concludes with a discussion.

\section{Bootstrap Method for Constructing Confidence Intervals}
\label{Bootstrap Method for Constructing Confidence Intervals}

\section{Shape Restricted Example}
\label{Shape Restricted Example}

\section{Simulation Study}
\label{Simulation Study}

\section{Conclusion}
\label{Conclusion}

\bibliographystyle{asa}
\bibliography{citations}

\end{document}

### 2023-07-30 Manuscript/Intro.tex
Update Intro.tex

@@
 \begin{abstract}
-The bootstrap method is an important resampling technique used to estimate statistics on a population by repeatedly sampling the data.
-It is also an effective approach for estimating the measure of dispersion in a dataset, especially in regression analysis.
-However, in some cases, regression models need to be constrained with known characteristics such as monotonicity or curvature, for example, in growth curves, where the coefficients are forced to be non-negative.
-In such situations, spline regression is used for modeling.
-It is not always certain whether the bootstrap method can be directly applied to estimate the dispersion under these shape-restricted scenarios, especially for pointwise confidence intervals.
-In this article, we will demonstrate the usage of the bootstrap method in shape-restricted regression and proof the effectiveness of bootstrap for constructing pointwise confidence intervals in shape-restricted regression empirically.
+The bootstrap method is an important resampling technique used to estimate 
+statistics on a population by repeatedly sampling the data. It is also an 
+effective approach for estimating the measure of dispersion in a dataset, 
+especially in regression analysis. However, in some cases, regression models 
+need to be constrained with known characteristics such as monotonicity or 
+curvature, for example, in growth curves, where the coefficients are forced
+to be non-negative. In such situations, spline regression is used for modeling.
+It is not always certain whether the bootstrap method can be directly applied 
+to estimate the dispersion under these shape-restricted scenarios, especially 
+for pointwise confidence intervals. In this article, we will demonstrate the 
+usage of the bootstrap method in shape-restricted regression and proof the 
+effectiveness of bootstrap for constructing pointwise confidence intervals 
+in shape-restricted regression empirically.
 \end{abstract}
@@
 \noindent%
-{\it Keywords:}  bootstrap; shape-restricted regression; pointwise confidence interval; growth curve; splines regression
+{\it Keywords:}  bootstrap; shape-restricted regression; pointwise confidence
+interval; growth curve; splines regression
 \vfill
@@
 
-Bootstrap is a powerful and important resampling method for estimating population parameters or assessing the accuracy of a statistical procedure by repeatedly sampling the data with replacement.
-Its effectiveness have been widely recognized in regression analysis.
-By bootstrap, we can estimate the standard errors of the regression coefficients.
-Even for unknown underlying population distributions, bootstrap method can resample the data with replacement and computes the regression coefficients for each resampled dataset.
-By repeating this process many times, it provides an empirical estimate of the standard errors, which can be valuable when the assumptions of traditional standard error estimation techniques are violated.
-It can also be used to construct confidence intervals for regression coefficients.
-By resampling the dataset, bootstrap can determining the percentile intervals of these coefficients, we can obtain approximate confidence intervals for the regression parameters.
-Bootstrap can also construct the approximate confidence interval for certain time points f(t)s in the function by simulating f'(t) certain times in certain time points.
-However, when dealing with shape-restricted regressions, where the coefficients are forced to adhere to specific constraints such as monotonicity or curvature, the effectiveness of bootstrap is not proved to be guaranteed.
-In this paper, we will demonstrate the usage of the bootstrap method in shape-restricted regression and proof the effectiveness of bootstrap for constructing pointwise confidence intervals in shape-restricted regression empirically.
+Bootstrap is a powerful and important resampling method for estimating 
+population parameters or assessing the accuracy of a statistical procedure
+by repeatedly sampling the data with replacement. Its effectiveness have 
+been widely recognized in regression analysis. By bootstrap, we can 
+estimate the standard errors of the regression coefficients. Even for
+unknown underlying population distributions, bootstrap method can resample
+the data with replacement and computes the regression coefficients for 
+each resampled dataset. By repeating this process many times, it provides
+an empirical estimate of the standard errors, which can be valuable when
+the assumptions of traditional standard error estimation techniques are 
+violated. It can also be used to construct confidence intervals for 
+regression coefficients. By resampling the dataset, bootstrap can 
+determining the percentile intervals of these coefficients, we can obtain
+approximate confidence intervals for the regression parameters. Bootstrap
+can also construct the approximate confidence interval for certain time
+points f(t)s in the function by simulating f'(t) certain times in certain
+time points. However, when dealing with shape-restricted regressions, where
+the coefficients are forced to adhere to specific constraints such as monotonicity
+or curvature, the effectiveness of bootstrap is not proved to be guaranteed.
+In this paper, we will demonstrate the usage of the bootstrap method in 
+shape-restricted regression and proof the effectiveness of bootstrap for 
+constructing pointwise confidence intervals in shape-restricted regression empirically.
 
-The rest of the paper is organized as the follows.
-Section~\ref{Bootstrap Method for Constructing Confidence Intervals} gives a review of bootstrap method for constructing confidence intervals.
-Section~\ref{Shape Restricted Example} gives out a shape-restricted regression example and the usage of bootstrap to build the pointwise confidence intervals for certain time points.
-Section~\ref{Simulation Study} shows a simulation study to assess the performance of the methods.
-explores the case where a combination of the first two scenarios occurs. An  
-adjusted bootstrap procedure is proposed as a working solution in this case.  
-Section~\ref{Conclusion} concludes with a discussion.
+The rest of the paper is organized as the follows. Section 
+~\ref{Bootstrap Method for Constructing Confidence Intervals} gives a review of 
+bootstrap method for constructing confidence intervals. 
+Section~\ref{Shape Restricted Example} gives out a shape-restricted regression example
+and the usage of bootstrap to build the pointwise confidence intervals for certain time
+points. Section~\ref{Simulation Study} shows a simulation study to assess the 
+performance of the methods.
 

### 2023-07-31 Manuscript/Manuscript.tex
Add files via upload

--- 2023-07-30 Manuscript/Intro.tex
@@
+\documentclass[12pt]{article}
 \usepackage{graphicx} 
-\documentclass[12pt]{article}
 \usepackage{amsmath}
@@
 \addtolength{\topmargin}{-.8in}%
+\usepackage{float}
+\usepackage{array}
 
@@
 
+The bootstrap method is a powerful resampling technique used to construct confidence intervals for population parameters or estimates when the underlying distribution is unknown or difficult to determine.
+It is useful in regression analysis to estimate the uncertainty associated with the regression coefficients or for certain time points inside the regression function.
+Specifically, the bootstrap method basically contains three steps:
+
+\begin{enumerate}[label=\arabic*.]
+    \item Let \(v\) represent a population parameter of interest (e.g., mean, median, standard deviation, etc.), which is drawn from an unknown population distribution \(F\).
+    \item Generate a bootstrap sample \(x_1, x_2, \ldots, x_n\) from the population, and they are referred to as the original sample dataset.
+    \item Let \(u\) represent a statistic calculated from the bootstrap original sample dataset.
+    \item Using the data in the original sample dataset as the "population," perform nonparametric resampling with replacement to obtain a resampled sample (also known as the Bootstrap sample), denoted as \(x_1^*, x_2^*, \ldots, x_n^*\) (the number of data points in the Bootstrap sample must be the same as the number of data points in the original sample).
+    \item Let \(u^*\) represent the statistic computed by the Bootstrap sample datasets, and this will be the bootstrap estimated statistic for the population statistic.
+
+\end{enumerate}
+
+Bootstrap method has been proved that it is an excellent method to estimate statistic, the \(u^*\) we obtained from the resampling dataset is a good estimator for the \(v\) as a population parameter.
+According to the bootstrap method, we can also calculate the confidence interval for the parameters, or the coefficients of a certain regression, or for certain time points in the regression.
+
+Should I give out an example for a normal regression and calculate its pointwise confidence interval by certain time points?
+
+It has been proved that the bootstrap method can be used as a good estimator for the pointwise confidence interval in linear regressions and non-linear regressions, but in certain special cases(i.e.
+shape-restricted splines regressions) we have not prove that it is a good method to build pointwise confidence interval via bootstrap.
+
+Shape-restricted splines regressions are piecewise polynominal, differentiable to a certain degree and have certain restrictions like monotonicity or convexity.
+Given these conditions, the application of the bootstrap method to estimate pointwise confidence intervals for specific time points within the regression cannot be guaranteed to be suitable.
+And in the article we gives out an example of shape-restricted regression and the method to fit confidence interval for certain time points in the function.
+
 \section{Shape Restricted Example}
 \label{Shape Restricted Example}
+
+In some situations the regression is forced to be shape-restricted to improve the predictive performance and reduce overfitting if the underlying regression function takes the specific form.
+The example is given from R package SemiPar.
+And we fit the shape-restricted regression by the R package Splines2.
+Splines2 provides implementation of those spline basis functions via R language, and we use that to build a non-decreasing curve by i-spline that force the coefficients to be non-negative with degree of freedom = 6.
+
+Then, we selected 10 time points, denoted as $f(t)$, with equal intervals from the dataset.
+We performed bootstrap resampling 1000 times to obtain the 95\% quantile pointwise confidence interval for each points.
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=0.8\textwidth]{SemiparCI.png}
+  \caption{CI build for the shape-restricted regression}
+  \label{fig:semipar}
+\end{figure}
 
@@
 
+Since the underlying distribution is unknown, we need to perform a simulation study to test whether the fitted pointwise confidence interval is accurate for the regression.
+
+We define a function \(y = 0.25(x - 0.9)\) and randomly generate 1000 points \(x\) and its corresponding values \(y\) with added noise.
+The noise is added from a standard normal distribution with \(\mu = 0\) and standard deviation \(1\).
+Let the paired values \((x, y\text{ with noise})\) be the dataset, and then we know the true values of \(y\) as well.
+
+We fit shape-restricted i-splines regressions using different degrees of freedom (6, 10, 15) to the dataset.
+We select 10 equally spaced time points from the dataset and perform bootstrap resampling 1000 times to estimate the \(95\%\) quantile pointwise confidence intervals for each of the selected time points.
+We repeat this process 1000 times to see how many times these confidence intervals can contain the true result.
+The results are shown below:
+
+\begin{table}[ht]
+  \centering
+  \caption{Result}
+\begin{tabular}{|c|c|c|c|c|}
+    \hline
+\textbf{x} & \textbf{y} & \textbf{df\_6} & \textbf{df\_10} & \textbf{df\_15} \\
+    \hline
+    1 & 0.025 & 1 & 1 & 1 \\
+    \hline
+    4.22 & 0.831 & 1 & 1 & 1 \\
+    \hline
+    7.44 & 1.64 & 1 & 1 & 1 \\
+    \hline
+    10.7 & 2.44 & 1 & 1 & 1 \\
+    \hline
+    13.9 & 3.25 & 1 & 1 & 1 \\
+    \hline
+    17.1 & 4.05 & 0.999 & 1 & 1 \\
+    \hline
+    20.3 & 4.86 & 1 & 1 & 1 \\
+    \hline
+    23.6 & 5.66 & 1 & 1 & 1 \\
+    \hline
+    26.8 & 6.47 & 1 & 1 & 1 \\
+    \hline
+    30 & 7.28 & 1 & 1 & 1 \\
+    \hline
+  \end{tabular}
+\end{table}
+
 \section{Conclusion}
 \label{Conclusion}
+
+The bootstrap method is a valid method to build pointwise confidence interval for shape-restricted regressions.
 

### 2023-07-31 Manuscript/Manuscript.tex

@@
 \begin{abstract}
-The bootstrap method is an important resampling technique used to estimate statistics on a population by repeatedly sampling the data.
-It is also an effective approach for estimating the measure of dispersion in a dataset, especially in regression analysis.
-However, in some cases, regression models need to be constrained with known characteristics such as monotonicity or curvature, for example, in growth curves, where the coefficients are forced to be non-negative.
-In such situations, spline regression is used for modeling.
-It is not always certain whether the bootstrap method can be directly applied to estimate the dispersion under these shape-restricted scenarios, especially for pointwise confidence intervals.
-In this article, we will demonstrate the usage of the bootstrap method in shape-restricted regression and proof the effectiveness of bootstrap for constructing pointwise confidence intervals in shape-restricted regression empirically.
+The bootstrap method is an important resampling technique used to estimate 
+statistics on a population by repeatedly sampling the data. It is also an 
+effective approach for estimating the measure of dispersion in a dataset,
+especially in regression analysis. However, in some cases, regression 
+models need to be constrained with known characteristics such as monotonicity
+or curvature, for example, in growth curves, where the coefficients are 
+forced to be non-negative. In such situations, spline regression is used 
+for modeling. It is not always certain whether the bootstrap method can 
+be directly applied to estimate the dispersion under these shape-restricted
+scenarios, especially for pointwise confidence intervals. In this article,
+we will demonstrate the usage of the bootstrap method in shape-restricted
+regression and proof the effectiveness of bootstrap for constructing 
+pointwise confidence intervals in shape-restricted regression empirically.
 \end{abstract}
@@
 \noindent%
-{\it Keywords:}  bootstrap; shape-restricted regression; pointwise confidence interval; growth curve; splines regression
+{\it Keywords:}  bootstrap; shape-restricted regression; pointwise confidence interval;
+growth curve; splines regression
 \vfill
@@
 
-Bootstrap is a powerful and important resampling method for estimating population parameters or assessing the accuracy of a statistical procedure by repeatedly sampling the data with replacement.
-Its effectiveness have been widely recognized in regression analysis.
-By bootstrap, we can estimate the standard errors of the regression coefficients.
-Even for unknown underlying population distributions, bootstrap method can resample the data with replacement and computes the regression coefficients for each resampled dataset.
-By repeating this process many times, it provides an empirical estimate of the standard errors, which can be valuable when the assumptions of traditional standard error estimation techniques are violated.
-It can also be used to construct confidence intervals for regression coefficients.
-By resampling the dataset, bootstrap can determining the percentile intervals of these coefficients, we can obtain approximate confidence intervals for the regression parameters.
-Bootstrap can also construct the approximate confidence interval for certain time points f(t)s in the function by simulating f'(t) certain times in certain time points.
-However, when dealing with shape-restricted regressions, where the coefficients are forced to adhere to specific constraints such as monotonicity or curvature, the effectiveness of bootstrap is not proved to be guaranteed.
-In this paper, we will demonstrate the usage of the bootstrap method in shape-restricted regression and proof the effectiveness of bootstrap for constructing pointwise confidence intervals in shape-restricted regression empirically.
+Bootstrap is a powerful and important resampling method for estimating 
+population parameters or assessing the accuracy of a statistical procedure 
+by repeatedly sampling the data with replacement. Its effectiveness have 
+been widely recognized in regression analysis. By bootstrap, we can estimate 
+the standard errors of the regression coefficients. Even for unknown 
+underlying population distributions, bootstrap method can resample the data 
+with replacement and computes the regression coefficients for each resampled
+dataset. By repeating this process many times, it provides an empirical 
+estimate of the standard errors, which can be valuable when the assumptions 
+of traditional standard error estimation techniques are violated. It can 
+also be used to construct confidence intervals for regression coefficients.
+By resampling the dataset, bootstrap can determining the percentile intervals
+of these coefficients, we can obtain approximate confidence intervals for 
+the regression parameters. Bootstrap can also construct the approximate 
+confidence interval for certain time points f(t)s in the function by 
+simulating f'(t) certain times in certain time points. However, when dealing
+with shape-restricted regressions, where the coefficients are forced to adhere
+to specific constraints such as monotonicity or curvature, the effectiveness
+of bootstrap is not proved to be guaranteed. In this paper, we will 
+demonstrate the usage of the bootstrap method in shape-restricted regression 
+and proof the effectiveness of bootstrap for constructing pointwise confidence
+intervals in shape-restricted regression empirically.
 
 The rest of the paper is organized as the follows. 
-Section~\ref{Bootstrap Method for Constructing Confidence Intervals} gives a review of bootstrap method for constructing confidence intervals.
-Section~\ref{Shape Restricted Example} gives out a shape-restricted regression example and the usage of bootstrap to build the pointwise confidence intervals for certain time points.
-Section~\ref{Simulation Study} shows a simulation study to assess the performance of the methods.
-explores the case where a combination of the first two scenarios occurs. An  
-adjusted bootstrap procedure is proposed as a working solution in this case.  
+Section~\ref{Bootstrap Method for Constructing Confidence Intervals}
+gives a review of bootstrap method for constructing confidence intervals
+. Section~\ref{Shape Restricted Example} gives out a shape-restricted regression
+example and the usage of bootstrap to build the pointwise confidence intervals
+for certain time points. Section~\ref{Simulation Study} shows a simulation 
+study to assess the performance of the methods. 
 Section~\ref{Conclusion} concludes with a discussion.
@@
 
-The bootstrap method is a powerful resampling technique used to construct confidence intervals for population parameters or estimates when the underlying distribution is unknown or difficult to determine.
-It is useful in regression analysis to estimate the uncertainty associated with the regression coefficients or for certain time points inside the regression function.
-Specifically, the bootstrap method basically contains three steps:
+The bootstrap method is a powerful resampling technique used to construct 
+confidence intervals for population parameters or estimates when the 
+underlying distribution is unknown or difficult to determine. It is useful
+in regression analysis to estimate the uncertainty associated with the 
+regression coefficients or for certain time points inside the regression 
+function. Specifically, the bootstrap method basically contains three steps:
 
 \begin{enumerate}[label=\arabic*.]
-    \item Let \(v\) represent a population parameter of interest (e.g., mean, median, standard deviation, etc.), which is drawn from an unknown population distribution \(F\).
-    \item Generate a bootstrap sample \(x_1, x_2, \ldots, x_n\) from the population, and they are referred to as the original sample dataset.
-    \item Let \(u\) represent a statistic calculated from the bootstrap original sample dataset.
-    \item Using the data in the original sample dataset as the "population," perform nonparametric resampling with replacement to obtain a resampled sample (also known as the Bootstrap sample), denoted as \(x_1^*, x_2^*, \ldots, x_n^*\) (the number of data points in the Bootstrap sample must be the same as the number of data points in the original sample).
-    \item Let \(u^*\) represent the statistic computed by the Bootstrap sample datasets, and this will be the bootstrap estimated statistic for the population statistic.
+    \item Let \(v\) represent a population parameter of interest 
+(e.g., mean, median, standard deviation, etc.), which is drawn from an unknown 
+population distribution \(F\).
+    \item Generate a bootstrap sample \(x_1, x_2, \ldots, x_n\) 
+from the population, and they are referred to as the original sample dataset.
+    \item Let \(u\) represent a statistic calculated from the bootstrap
+original sample dataset.
+    \item Using the data in the original sample dataset as the "population,"
+perform nonparametric resampling with replacement to obtain a resampled sample
+(also known as the Bootstrap sample), denoted as \(x_1^*, x_2^*, \ldots, x_n^*\)
+(the number of data points in the Bootstrap sample must be the same as the number 
+of data points in the original sample).
+    \item Let \(u^*\) represent the statistic computed by the Bootstrap sample 
+datasets, and this will be the bootstrap estimated statistic for the population statistic.
 
@@
 
-Bootstrap method has been proved that it is an excellent method to estimate statistic, the \(u^*\) we obtained from the resampling dataset is a good estimator for the \(v\) as a population parameter.
-According to the bootstrap method, we can also calculate the confidence interval for the parameters, or the coefficients of a certain regression, or for certain time points in the regression.
+Bootstrap method has been proved that it is an excellent method to estimate 
+statistic, the \(u^*\) we obtained from the resampling dataset is a good 
+estimator for the \(v\) as a population parameter. According to the bootstrap
+method, we can also calculate the confidence interval for the parameters, or the
+coefficients of a certain regression, or for certain time points in the regression.
 
-Should I give out an example for a normal regression and calculate its pointwise confidence interval by certain time points?
+Should I give out an example for a normal regression and calculate its 
+pointwise confidence interval by certain time points?
 
-It has been proved that the bootstrap method can be used as a good estimator for the pointwise confidence interval in linear regressions and non-linear regressions, but in certain special cases(i.e.
-shape-restricted splines regressions) we have not prove that it is a good method to build pointwise confidence interval via bootstrap.
+It has been proved that the bootstrap method can be used as a good estimator 
+for the pointwise confidence interval in linear regressions and non-linear 
+regressions, but in certain special cases(i.e. shape-restricted splines 
+regressions) we have not prove that it is a good method to build pointwise 
+confidence interval via bootstrap.
 
-Shape-restricted splines regressions are piecewise polynominal, differentiable to a certain degree and have certain restrictions like monotonicity or convexity.
-Given these conditions, the application of the bootstrap method to estimate pointwise confidence intervals for specific time points within the regression cannot be guaranteed to be suitable.
-And in the article we gives out an example of shape-restricted regression and the method to fit confidence interval for certain time points in the function.
+Shape-restricted splines regressions are piecewise polynominal, 
+differentiable to a certain degree and have certain restrictions like 
+monotonicity or convexity. Given these conditions, the application of 
+the bootstrap method to estimate pointwise confidence intervals for 
+specific time points within the regression cannot be guaranteed to 
+be suitable. And in the article we gives out an example of 
+shape-restricted regression and the method to fit confidence interval
+for certain time points in the function.
 
@@
 
-In some situations the regression is forced to be shape-restricted to improve the predictive performance and reduce overfitting if the underlying regression function takes the specific form.
-The example is given from R package SemiPar.
-And we fit the shape-restricted regression by the R package Splines2.
-Splines2 provides implementation of those spline basis functions via R language, and we use that to build a non-decreasing curve by i-spline that force the coefficients to be non-negative with degree of freedom = 6.
+In some situations the regression is forced to be shape-restricted to improve 
+the predictive performance and reduce overfitting if the underlying regression
+function takes the specific form. The example is given from R package SemiPar.
+And we fit the shape-restricted regression by the R package Splines2. Splines2
+provides implementation of those spline basis functions via R language, and 
+we use that to build a non-decreasing curve by i-spline that force the 
+coefficients to be non-negative with degree of freedom = 6.
 
-Then, we selected 10 time points, denoted as $f(t)$, with equal intervals from the dataset.
-We performed bootstrap resampling 1000 times to obtain the 95\% quantile pointwise confidence interval for each points.
+Then, we selected 10 time points, denoted as $f(t)$, with equal intervals 
+from the dataset. We performed bootstrap resampling 1000 times to obtain the 
+95\% quantile pointwise confidence interval for each points.
 
@@
 
-Since the underlying distribution is unknown, we need to perform a simulation study to test whether the fitted pointwise confidence interval is accurate for the regression.
+Since the underlying distribution is unknown, we need to perform a simulation
+study to test whether the fitted pointwise confidence interval is accurate for 
+the regression.
 
-We define a function \(y = 0.25(x - 0.9)\) and randomly generate 1000 points \(x\) and its corresponding values \(y\) with added noise.
-The noise is added from a standard normal distribution with \(\mu = 0\) and standard deviation \(1\).
-Let the paired values \((x, y\text{ with noise})\) be the dataset, and then we know the true values of \(y\) as well.
+We define a function \(y = 0.25(x - 0.9)\) and randomly generate 1000 points
+\(x\) and its corresponding values \(y\) with added noise. The noise is added 
+from a standard normal distribution with \(\mu = 0\) and standard deviation
+\(1\). Let the paired values \((x, y\text{ with noise})\) be the dataset, 
+and then we know the true values of \(y\) as well.
 
-We fit shape-restricted i-splines regressions using different degrees of freedom (6, 10, 15) to the dataset.
-We select 10 equally spaced time points from the dataset and perform bootstrap resampling 1000 times to estimate the \(95\%\) quantile pointwise confidence intervals for each of the selected time points.
-We repeat this process 1000 times to see how many times these confidence intervals can contain the true result.
-The results are shown below:
+We fit shape-restricted i-splines regressions using different degrees of 
+freedom (6, 10, 15) to the dataset. We select 10 equally spaced time points
+from the dataset and perform bootstrap resampling 1000 times to estimate 
+the \(95\%\) quantile pointwise confidence intervals for each of the selected
+time points. We repeat this process 1000 times to see how many times these 
+confidence intervals can contain the true result. The results are shown below:
 
@@
 
-The bootstrap method is a valid method to build pointwise confidence interval for shape-restricted regressions.
+The bootstrap method is a valid method to build pointwise confidence interval 
+for shape-restricted regressions.
 

### 2023-07-31 Code/demo.R
demo structure for simulation

@@ -1,0 +1,24 @@
+
+## for each given dataset and sequence of times, return CI for
+## f(t) at the given time points
+
+ci1rep <- function(tis, df = 6, conf.level = .95) {
+    ## generate data: x and y given f(t), noise variance
+    
+    ## fit f(x) given (x, y) and estimate theta (point estimate)
+
+    ## bootstrap 1000 times, and obtain theta_b, b = 1, \ldots, B
+    ## Put them in a B by df matrix
+ 
+    ## construct CI for each f(t), t in tis (length lt)
+    ## return ciFts # alt x 2 matrix
+
+    ## vector of TRUE/FALSE of length lt
+    
+}
+
+
+nrep <- 1000
+sim <- replicate(nrep, ci1rep(tis))
+
+

### 2023-08-13 Manuscript/manuscript.tex

--- 2023-07-31 Manuscript/Manuscript.tex
@@
 The example is given from R package SemiPar.
-And we fit the shape-restricted regression by the R package Splines2.
+And we fit the shape-restricted regression by the R package Splines2 based on the article \cite{wang2021shape}.
 Splines2 provides implementation of those spline basis functions via R language, and we use that to build a non-decreasing curve by i-spline that force the coefficients to be non-negative with degree of freedom = 6.
@@
 
-We define a function \(y = 0.25(x - 0.9)\) and randomly generate 1000 points \(x\) and its corresponding values \(y\) with added noise.
+We define three functions: \(y = 0.25(x - 0.9)\) , \(y = 0.02(x^3+1.2)\) , and \( y = 0.1 (5pnorm((x - 2) / 0.3) + 1)\) , and randomly generate 1000 points \(x\) and its corresponding values \(y\) with added noise.
 The noise is added from a standard normal distribution with \(\mu = 0\) and standard deviation \(1\).
@@
 
-We fit shape-restricted i-splines regressions using different degrees of freedom (6, 10, 15) to the dataset.
-We select 10 equally spaced time points from the dataset and perform bootstrap resampling 1000 times to estimate the \(95\%\) quantile pointwise confidence intervals for each of the selected time points.
+We fit shape-restricted i-splines regressions using degrees of freedom 6 to the dataset.
+We select 1, 5, 10, 15, 20, 25, 30 as the time points from the dataset and perform bootstrap resampling B = 1000 times to estimate the \(95\%\) quantile pointwise confidence intervals for each of the selected time points.
 We repeat this process 1000 times to see how many times these confidence intervals can contain the true result.
@@
   \centering
-  \caption{Result}
+  \caption{Results of function \(y = 0.25(x - 0.9)\) for different degrees of freedom}
   \begin{tabular}{|c|c|c|c|c|}
@@
     \hline
-    1 & 0.025 & 1 & 1 & 1 \\
+    \multicolumn{5}{|c|}{B = 1000} \\
     \hline
-    4.22 & 0.831 & 1 & 1 & 1 \\
+    1 & 0.025 & 0.936 & 0.944 & 0.939 \\
     \hline
-    7.44 & 1.64 & 1 & 1 & 1 \\
+    5 & 1.025 & 0.960 & 0.958 & 0.948 \\
     \hline
-    10.7 & 2.44 & 1 & 1 & 1 \\
+    10 & 2.275 & 0.956 & 0.950 & 0.951 \\
     \hline
-    13.9 & 3.25 & 1 & 1 & 1 \\
+    15 & 3.525 & 0.959 & 0.954 & 0.954 \\
     \hline
-    17.1 & 4.05 & 0.999 & 1 & 1 \\
+    20 & 4.775 & 0.941 & 0.949 & 0.961 \\
     \hline
-    20.3 & 4.86 & 1 & 1 & 1 \\
+    25 & 6.025 & 0.953 & 0.946 & 0.942 \\
     \hline
-    23.6 & 5.66 & 1 & 1 & 1 \\
+    30 & 7.275 & 0.919 & 0.955 & 0.947 \\
     \hline
-    26.8 & 6.47 & 1 & 1 & 1 \\
+    \multicolumn{5}{|c|}{B = 2000} \\
     \hline
-    30 & 7.28 & 1 & 1 & 1 \\
+    1 & 0.025 & 0.936 & 0.944 & 0.939 \\
+    \hline
+    5 & 1.025 & 0.960 & 0.958 & 0.948 \\
+    \hline
+    10 & 2.275 & 0.956 & 0.950 & 0.951 \\
+    \hline
+    15 & 3.525 & 0.959 & 0.954 & 0.954 \\
+    \hline
+    20 & 4.775 & 0.941 & 0.949 & 0.961 \\
+    \hline
+    25 & 6.025 & 0.953 & 0.946 & 0.942 \\
+    \hline
+    30 & 7.275 & 0.919 & 0.955 & 0.947 \\
+    \hline
+  \end{tabular}
+\end{table}
+
+\begin{table}[ht]
+  \centering
+  \caption{Result of function  \(y = 0.02(x^3+1.2)\)}
+\begin{tabular}{|c|c|c|c|c|}
+    \hline
+\textbf{x} & \textbf{y} & \textbf{df\_6} & \textbf{df\_10} & \textbf{df\_15} \\
+    \hline
+    1 & 0.025 & 0.893 & 0.940 & 0.959 \\
+    \hline
+    5 & 1.025 & 0.932 & 0.948 & 0.958 \\
+    \hline
+    10 & 2.275 & 0.937 & 0.948 & 0.941 \\
+    \hline
+    15 & 3.525 & 0.942 & 0.951 & 0.953 \\
+    \hline
+    20 & 4.775 & 0.939 & 0.951 & 0.957 \\
+    \hline
+    25 & 6.025 & 0.952 & 0.959 & 0.963 \\
+    \hline
+    30 & 7.275 & 0.947 & 0.943 & 0.943 \\
+    \hline
+  \end{tabular}
+\end{table}
+
+\begin{table}[ht]
+  \centering
+  \caption{Result of function \( y = 0.1 (5pnorm((x - 2) / 0.3) + 1)\) when B = 1000}
+\begin{tabular}{|c|c|c|c|c|}
+    \hline
+\textbf{x} & \textbf{y} & \textbf{df\_6} & \textbf{df\_10} & \textbf{df\_15} \\
+    \hline
+    1 & 0.025 & 0.686 & 0.847 & 0.901 \\
+    \hline
+    5 & 1.025 & 0.279 & 0.800 & 0.852 \\
+    \hline
+    10 & 2.275 & 0.947 & 0.937 & 0.942 \\
+    \hline
+    15 & 3.525 & 0.937 & 0.953 & 0.961 \\
+    \hline
+    20 & 4.775 & 0.929 & 0.950 & 0.957 \\
+    \hline
+    25 & 6.025 & 0.953 & 0.924 & 0.922 \\
+    \hline
+    30 & 7.275 & 0.919 & 0.858 & 0.832 \\
     \hline
@@
 
-The bootstrap method is a valid method to build pointwise confidence interval for shape-restricted regressions.
+In all those functions and degrees of freedom we have given, the bootstrap method gives pointwise confidence intervals that are close to 95 \% .
+As the number of bootstrap samples \(B\) increases, the performance improves as expected, particularly for those points where the method initially showed lower performance.
+Therefore, we can conclude that the bootstrap method is a valid approach for constructing pointwise confidence intervals in the context of shape-restricted regressions.
 
-\bibliographystyle{asa}
+\bibliographystyle{plain}
 \bibliography{citations}

### 2023-08-14 Code/Bootstrap and Simulation.R
Delete Bootstrap and Simulation.R

@@ -1,363 +1,0 @@
-library(splines2)
-library(quadprog)
-library(boot)
-library(SemiPar)
-library(plotrix)
-library(tidyverse)
-library(ggthemes)
-
-standardize <- function(x, y) {
-  sx <- scale(x); sy <- scale(y)
-  x_bar <- attr(sx, "scaled:center"); x_sd <- attr(sx, "scaled:scale")
-  y_bar <- attr(sy, "scaled:center"); y_sd <- attr(sy, "scaled:scale")
-  list(sx = sx, x_bar = x_bar, x_sd = x_sd,
-       sy = sy, y_bar = y_bar, y_sd = y_sd)
-}
-
-qp_solve <- function(standardized, A_mat, x_mat, ...) {
-  d_vec <- with(standardized, crossprod(sx, sy)) 
-  D_mat <- crossprod(standardized$sx) 
-  sbeta <- quadprog::solve.QP(D_mat, d_vec, A_mat, ...)$solution
-  
-  beta0 <- with(standardized,
-                -as.numeric(crossprod(x_bar * y_sd / x_sd, sbeta)) + y_bar)
-  beta1 <- with(standardized, y_sd / x_sd * sbeta)
-  list(x_mat = x_mat,
-       coefficients = c("(Intercept)" = beta0, beta1),
-       fitted = as.numeric(x_mat %*% beta1) + beta0)
-}
-
-mono_fit <- function(x, y, monotone = c("increasing", "decreasing"), ...) {
-  monotone <- match.arg(monotone)
-  x_mat <- iSpline(x, ..., intercept = TRUE) 
-  standardized <- standardize(x_mat, y)
-  A_mat <- diag(ncol(standardized$sx)) 
-  if (monotone == "decreasing") A_mat <- -A_mat 
-  qp_solve(standardized, A_mat, x_mat)
-}
-
-data(age.income, package = "SemiPar")
-dfs <- c(6)
-mfits <- lapply(dfs, function(d) {
-  with(age.income, mono_fit(age, log.income, df = d))
-})
-
-curv_fit <- function(x, y, monotone = c("none", "increasing", "decreasing"),
-                     curvature = c("convex", "concave"), ...) {
-  monotone <- match.arg(monotone); curvature <- match.arg(curvature)
-  min_x <- min(x); range_x <- max(x) - min_x
-  x_mat <- cSpline(x, ..., intercept = TRUE) 
-  if (monotone != "none") {
[…]

### 2023-08-14 Manuscript/manuscript.tex

@@
 It is also an effective approach for estimating the measure of dispersion in a dataset, especially in regression analysis.
-However, in some cases, regression models need to be constrained with known characteristics such as monotonicity or curvature, for example, in growth curves, where the coefficients are forced to be non-negative.
+Meanwhile, the bootstrap method is also a valid method for constructing pointwise confidence intervals for time points in regressions.
+However, in some special cases, regression models need to be constrained with known characteristics such as monotonicity or curvature, for example, in growth curves, where the coefficients are forced to be non-negative.
 In such situations, spline regression is used for modeling.
@@
 Bootstrap is a powerful and important resampling method for estimating population parameters or assessing the accuracy of a statistical procedure by repeatedly sampling the data with replacement.
-Its effectiveness have been widely recognized in regression analysis.
-By bootstrap, we can estimate the standard errors of the regression coefficients.
+Its effectiveness have been widely recognized in linear regression analysis \cite{efron1979bootstrap}, and non-linear regression analysis \cite{davidson1999bootstrap}.
+By bootstrap method, we can estimate the standard errors of the regression coefficients.
 Even for unknown underlying population distributions, bootstrap method can resample the data with replacement and computes the regression coefficients for each resampled dataset.
-By repeating this process many times, it provides an empirical estimate of the standard errors, which can be valuable when the assumptions of traditional standard error estimation techniques are violated.
-It can also be used to construct confidence intervals for regression coefficients.
-By resampling the dataset, bootstrap can determining the percentile intervals of these coefficients, we can obtain approximate confidence intervals for the regression parameters.
-Bootstrap can also construct the approximate confidence interval for certain time points f(t)s in the function by simulating f'(t) certain times in certain time points.
-However, when dealing with shape-restricted regressions, where the coefficients are forced to adhere to specific constraints such as monotonicity or curvature, the effectiveness of bootstrap is not proved to be guaranteed.
+\cite{hall2013simple}By repeating this process many times, it provides a valid empirical estimate of the standard errors in both linear cases \cite{efron1985bootstrap} and nonlinear cases\cite{wong2019bootstrap}, thus it is valuable when the assumptions of traditional standard error estimation techniques are violated.
+It is also a valid method used to construct confidence intervals for regression coefficients.
+\cite{efron1985bootstrap}By resampling the dataset, bootstrap can determining the percentile intervals of these coefficients, and also can obtain approximate confidence intervals for the regression parameters.
+\cite{cui2012evaluating} Bootstrap can also construct the approximate confidence interval for certain time points f(t)s in the function by simulating f'(t) certain times in certain time points.
+\cite{horowitz2018bootstrap} However, when dealing with shape-restricted regressions, where the coefficients are forced to adhere to specific constraints such as monotonicity or curvature, the effectiveness of bootstrap is not proved to be guaranteed.
 In this paper, we will demonstrate the usage of the bootstrap method in shape-restricted regression and proof the effectiveness of bootstrap for constructing pointwise confidence intervals in shape-restricted regression empirically.
@@
 The bootstrap method is a powerful resampling technique used to construct confidence intervals for population parameters or estimates when the underlying distribution is unknown or difficult to determine.
-It is useful in regression analysis to estimate the uncertainty associated with the regression coefficients or for certain time points inside the regression function.
+\cite{hall2013simple}It is useful in regression analysis to estimate the uncertainty associated with the regression coefficients or for certain time points inside the regression function.
 Specifically, the bootstrap method basically contains three steps:
@@
 
-Bootstrap method has been proved that it is an excellent method to estimate statistic, the \(u^*\) we obtained from the resampling dataset is a good estimator for the \(v\) as a population parameter.
+Bootstrap method has been proved that it is an excellent method to estimate statistic \cite{efron1979bootstrap}, the \(u^*\) we obtained from the resampling dataset is a good estimator for the \(v\) as a population parameter.
 According to the bootstrap method, we can also calculate the confidence interval for the parameters, or the coefficients of a certain regression, or for certain time points in the regression.
+In this article, we will focus on the method of construct a pointwise confidence interval by bootstrap.
+To construct a pointwise confidence interval using the bootstrap method, the procedure involves the following steps:
 
-Should I give out an example for a normal regression and calculate its pointwise confidence interval by certain time points?
+\begin{enumerate}[label=\arabic*.]
+    \item First we observed a specific time point \(t\) that we are interested and its corresponding true value \(f(t)\), and build them as a pair \(t, f(t)\).
+    \item According to the dataset, fit \(\hat{f}\) as the estimated regression for the dataset.
+    \item Generate a bootstrap sample \(x_1, x_2, \ldots, x_n\) from the population by sampling with replacement, and they are referred to as the original sample dataset. 
+    \item Then  \( [\hat{f}_n(t) - \hat{q}_{1-\alpha/2,n-1/3}, \hat{f}_n(t) - \hat{q}_{\alpha/2,n-1/3} ]\)  would be the bootstrap estimated pointwise confidence interval where \(\hat{q}_\alpha\) denoted the \(\alpha\)th quantile of the time point \(t\).
 
-It has been proved that the bootstrap method can be used as a good estimator for the pointwise confidence interval in linear regressions and non-linear regressions, but in certain special cases(i.e.
-shape-restricted splines regressions) we have not prove that it is a good method to build pointwise confidence interval via bootstrap.
+\end{enumerate}
 
-Shape-restricted splines regressions are piecewise polynominal, differentiable to a certain degree and have certain restrictions like monotonicity or convexity.
-Given these conditions, the application of the bootstrap method to estimate pointwise confidence intervals for specific time points within the regression cannot be guaranteed to be suitable.
-And in the article we gives out an example of shape-restricted regression and the method to fit confidence interval for certain time points in the function.
+It has been proved that the bootstrap method can be used as a good estimator for the pointwise confidence interval in linear regressions and non-linear regressions\cite{efron1979bootstrap}\cite{davidson1999bootstrap}, and some examples in certain configurations are given.\cite{ruhe2019bootstrap}\cite{ma2019inference}\cite{dugas2010pointwise} But in certain special cases(i.e.
+shape-restricted splines regressions) there is no certain resource have not prove that it is a good method to build pointwise confidence interval via bootstrap.
+
+Shape-restricted splines regressions are piecewise polynominal, differentiable to a certain degree and have certain restrictions like monotonicity or convexity.\cite{meyer2008inference} Given these conditions, the application of the bootstrap method to estimate pointwise confidence intervals for specific time points within the regression cannot be guaranteed to be suitable.
+And in the rest of the article we gives out an example of shape-restricted regression and the method to fit confidence interval for certain time points in the function.
 
@@
 In some situations the regression is forced to be shape-restricted to improve the predictive performance and reduce overfitting if the underlying regression function takes the specific form.
-The example is given from R package SemiPar.
-And we fit the shape-restricted regression by the R package Splines2 based on the article \cite{wang2021shape}.
-Splines2 provides implementation of those spline basis functions via R language, and we use that to build a non-decreasing curve by i-spline that force the coefficients to be non-negative with degree of freedom = 6.
-
-Then, we selected 10 time points, denoted as $f(t)$, with equal intervals from the dataset.
-We performed bootstrap resampling 1000 times to obtain the 95\% quantile pointwise confidence interval for each points.
+Some regressions are naturally constrained to convexity or concativity in a lot of disciplines like economics, biology, and psychological studies, and other ares.\cite{jieying2022heteroscedastic} \cite{guntuboyina2018nonparametric} Some popular examples like cost function and profit function in economics\cite{gallant1984imposing}, precipitation data analysis\cite{molitor2002bayesian}.
+In this article we gives out an example of the relationship between income and the age of Canadian workers.
+The data is given from R package SemiPar.
+For those situations, Regression splines are smooth, flexible, and parsimonious nonparametric function estimators, and it offers an effective approach to enhance the inference of shape-restricted regression.
+\cite{meyer2008inference} In this dataset, a nondecreasing relationship between the age of workers and the expected logarithm of the income was considered.
+\cite{wang2021shape}  Splines2 provides implementation of those spline basis functions via R language, and we use that to build a non-decreasing curve by i-spline that force the coefficients to be non-negative with degree of freedom = 6.
+Then, we selected 10 time points, denoted as $t$, with equal intervals from the dataset, corresponding to one of them is the regression time points \(f'(t)\) that fitted by iSpline.
+We also performed bootstrap resampling 1000 times to obtain the 95\% quantile pointwise confidence interval for each points.
+In the figure below, the red line represents the fitted i-spline regression, the yellow line is the smooth regression, and we build ten pointwise confidence intervals for 10 certain time points.
+The result is shown in Figure ~\ref{fig:semipar}.
 
@@
   \includegraphics[width=0.8\textwidth]{SemiparCI.png}
-  \caption{CI build for the shape-restricted regression}
+  \caption{CI build for the shape-restricted regression: The red line is the fitted i-splines regression, the yellow line is the smoothing splines, the grey area represents the \(95\%\) confidence interval for the smoothing splines, and the black solid intervals are the bootstrap pointwise confidence intervals for certain time points.
+}
   \label{fig:semipar}
 \end{figure}
+
+We can see that, for this one-time example all the pointwise confidence intervals constructed by the bootstrap method include the fitted regression.
+But it is not a valid proof that bootstrap is a good method for constructing pointwise confidence intervals since the regression is fitted by the dataset, and the criteria is given by \(f'(t)\) which is given by the regression but not the the true value \(f(t)\).
+In this case, a simulation study is required to further prove the effectiveness of bootstrap pointwise confidence intervals.
 
@@
 
-We define three functions: \(y = 0.25(x - 0.9)\) , \(y = 0.02(x^3+1.2)\) , and \( y = 0.1 (5pnorm((x - 2) / 0.3) + 1)\) , and randomly generate 1000 points \(x\) and its corresponding values \(y\) with added noise.
-The noise is added from a standard normal distribution with \(\mu = 0\) and standard deviation \(1\).
-Let the paired values \((x, y\text{ with noise})\) be the dataset, and then we know the true values of \(y\) as well.
+We define three functions: \(y = 0.25(x - 0.9)\) , \(y = 0.02(x^3+1.2)\) , and \( y = 0.1 (5\Phi((x - 2) / 0.3) + 1)\) , where \(\Phi\) is the cumulative distribution function of the standard normal distribution.
+For those functions, the validity of the bootstrap method to build the confidence intervals for the coefficients and standard error has already been proved.
+\cite{jieying2022heteroscedastic} And in this article we want to further prove the validity of the bootstrap method to build the pointwise confidence intervals for certain time points in the domain of the function.
+First of all, we randomly generate 1000 points \(x\) in the domain of \([0,30]\), and we calculate its corresponding values \(y(x)\), and make simulation data points \(f'(x)\) by add noise to the true value \(f(x)\).
+The noise is added from a standard normal distribution with \(\mu = 0\) and \(\sigma = \) \(1\).
+And then we make the paired values \((x, y\text{ with noise})\) be the dataset, while we know the true values of \(f(x)\) as well.
 
-We fit shape-restricted i-splines regressions using degrees of freedom 6 to the dataset.
-We select 1, 5, 10, 15, 20, 25, 30 as the time points from the dataset and perform bootstrap resampling B = 1000 times to estimate the \(95\%\) quantile pointwise confidence intervals for each of the selected time points.
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=0.8\textwidth]{DataAndRegressions.png}
+  \caption{The generated dataset, true functions and fitted i-splines regressions: the shaded green curve represents the true functions, the pink points are the data pair \((x, f'(x))\) where \(f'(x)\) is generated by \(f(x)\) add noise, and the red curves are the fitted i-splines regression curve with degrees of freedom\(= 6,10,15\), from top to bottom}
+  \label{fig:DataAndRegressions}
+\end{figure}
+
+We use quadratic i-splines function to enforce the monotonicity of the function and we picked degrees of freedom 6,10,15 to build the regression for the dataset.
+The generated dataset and regressions is shown in Figure ~\ref{fig:DataAndRegressions}.
+In each configuration, we select 1, 5, 10, 15, 20, 25, 30 as the time points from the dataset and perform bootstrap resampling 1000 times to estimate the \(95\%\) quantile pointwise confidence intervals for each of the selected time points.
 We repeat this process 1000 times to see how many times these confidence intervals can contain the true result.
-The results are shown below:
+The results are shown in Table ~\ref{Table}.
 
@@
   \centering
-  \caption{Results of function \(y = 0.25(x - 0.9)\) for different degrees of freedom}
+  \label{Table}
+  \caption{Results of functions for different degrees of freedom}
   \begin{tabular}{|c|c|c|c|c|}
     \hline
-    \textbf{x} & \textbf{y} & \textbf{df\_6} & \textbf{df\_10} & \textbf{df\_15} \\
+    \textbf{x} & \textbf{f(x)} & \textbf{CP of df\_6} & \textbf{CP of df\_10} & \textbf{CP of df\_15} \\
     \hline
-    \multicolumn{5}{|c|}{B = 1000} \\
+    \multicolumn{5}{|c|}{\(y = 0.25(x - 0.9)\)} \\
     \hline
@@
     \hline
-    \multicolumn{5}{|c|}{B = 2000} \\
-    \hline
-    1 & 0.025 & 0.936 & 0.944 & 0.939 \\
-    \hline
-    5 & 1.025 & 0.960 & 0.958 & 0.948 \\
-    \hline
-    10 & 2.275 & 0.956 & 0.950 & 0.951 \\
-    \hline
-    15 & 3.525 & 0.959 & 0.954 & 0.954 \\
-    \hline
-    20 & 4.775 & 0.941 & 0.949 & 0.961 \\
-    \hline
-    25 & 6.025 & 0.953 & 0.946 & 0.942 \\
-    \hline
-    30 & 7.275 & 0.919 & 0.955 & 0.947 \\
-    \hline
-  \end{tabular}
-\end{table}
-
-\begin{table}[ht]
-  \centering
-  \caption{Result of function  \(y = 0.02(x^3+1.2)\)}
-\begin{tabular}{|c|c|c|c|c|}
-    \hline
-\textbf{x} & \textbf{y} & \textbf{df\_6} & \textbf{df\_10} & \textbf{df\_15} \\
+    \multicolumn{5}{|c|}{\(y = 0.02(x^3+1.2)\)} \\
     \hline
@@
     \hline
-  \end{tabular}
-\end{table}
-
-\begin{table}[ht]
-  \centering
-  \caption{Result of function \( y = 0.1 (5pnorm((x - 2) / 0.3) + 1)\) when B = 1000}
-\begin{tabular}{|c|c|c|c|c|}
-    \hline
-\textbf{x} & \textbf{y} & \textbf{df\_6} & \textbf{df\_10} & \textbf{df\_15} \\
+    \multicolumn{5}{|c|}{\(y = 0.1 (5\Phi((x - 2) / 0.3) + 1)\)} \\
     \hline
@@
 
+In table ~\ref{Table}, \(x\) represents the certain time point we selected in the domain of the function, and \(f(x)\) is its true value calculated by the certain known function.
+CP represents coverage percentage of pointwise confidence interval we built by the bootstrap methods under certain degrees of freedom.
+We can see that in all those functions and degrees of freedom we have given, the bootstrap method gives pointwise confidence intervals coverage that are closed to the nominal level \(95\%\).
+
 \section{Conclusion}
 \label{Conclusion}
+In this study, we explored the application of the bootstrap method of building pointwise confidence intervals in shape-restricted cases.
+We demonstrated its effectiveness in constructing pointwise confidence intervals for certain time points within the regression function.
 
-In all those functions and degrees of freedom we have given, the bootstrap method gives pointwise confidence intervals that are close to 95 \% .
-As the number of bootstrap samples \(B\) increases, the performance improves as expected, particularly for those points where the method initially showed lower performance.
-Therefore, we can conclude that the bootstrap method is a valid approach for constructing pointwise confidence intervals in the context of shape-restricted regressions.
+We gives out a simulation study to prove that the pointwise confidence intervals constructed using the bootstrap method provide good empirical coverage for the true values of the regression function.
+This suggests that the bootstrap method is a valid approach for enhancing the inference of shape-restricted regressions, even for pointwise confidence intervals.
+
+Our findings support the utility of the bootstrap method to build the pointwise confidence intervals in cases where regression models have specific constraints such as monotonicity or curvature.
+However, it's important to consider the assumptions and limitations of the bootstrap method and validate its performance for specific datasets and applications.
 

### 2023-08-14 Manuscript/manuscript.tex
Update manuscript.tex

@@
 \begin{abstract}
-The bootstrap method is an important resampling technique used to estimate statistics on a population by repeatedly sampling the data.
-It is also an effective approach for estimating the measure of dispersion in a dataset, especially in regression analysis.
-Meanwhile, the bootstrap method is also a valid method for constructing pointwise confidence intervals for time points in regressions.
-However, in some special cases, regression models need to be constrained with known characteristics such as monotonicity or curvature, for example, in growth curves, where the coefficients are forced to be non-negative.
-In such situations, spline regression is used for modeling.
-It is not always certain whether the bootstrap method can be directly applied to estimate the dispersion under these shape-restricted scenarios, especially for pointwise confidence intervals.
-In this article, we will demonstrate the usage of the bootstrap method in shape-restricted regression and proof the effectiveness of bootstrap for constructing pointwise confidence intervals in shape-restricted regression empirically.
+The bootstrap method is an important resampling technique used to estimate 
+statistics on a population by repeatedly sampling the data. It is also an 
+effective approach for estimating the measure of dispersion in a dataset, 
+especially in regression analysis. Meanwhile, the bootstrap method is also
+a valid method for constructing pointwise confidence intervals for time 
+points in regressions. However, in some special cases, regression models 
+need to be constrained with known characteristics such as monotonicity or
+curvature, for example, in growth curves, where the coefficients are 
+forced to be non-negative. In such situations, spline regression is used
+for modeling. It is not always certain whether the bootstrap method can 
+be directly applied to estimate the dispersion under these shape-restricted
+scenarios, especially for pointwise confidence intervals. In this article,
+we will demonstrate the usage of the bootstrap method in shape-restricted 
+regression and proof the effectiveness of bootstrap for constructing 
+pointwise confidence intervals in shape-restricted regression empirically.
 \end{abstract}
@@
 \noindent%
-{\it Keywords:}  bootstrap; shape-restricted regression; pointwise confidence interval; growth curve; splines regression
+{\it Keywords:}  bootstrap; shape-restricted regression; 
+pointwise confidence interval; growth curve; splines regression
 \vfill
@@
 
-Bootstrap is a powerful and important resampling method for estimating population parameters or assessing the accuracy of a statistical procedure by repeatedly sampling the data with replacement.
-Its effectiveness have been widely recognized in linear regression analysis \cite{efron1979bootstrap}, and non-linear regression analysis \cite{davidson1999bootstrap}.
-By bootstrap method, we can estimate the standard errors of the regression coefficients.
-Even for unknown underlying population distributions, bootstrap method can resample the data with replacement and computes the regression coefficients for each resampled dataset.
-\cite{hall2013simple}By repeating this process many times, it provides a valid empirical estimate of the standard errors in both linear cases \cite{efron1985bootstrap} and nonlinear cases\cite{wong2019bootstrap}, thus it is valuable when the assumptions of traditional standard error estimation techniques are violated.
-It is also a valid method used to construct confidence intervals for regression coefficients.
-\cite{efron1985bootstrap}By resampling the dataset, bootstrap can determining the percentile intervals of these coefficients, and also can obtain approximate confidence intervals for the regression parameters.
-\cite{cui2012evaluating} Bootstrap can also construct the approximate confidence interval for certain time points f(t)s in the function by simulating f'(t) certain times in certain time points.
-\cite{horowitz2018bootstrap} However, when dealing with shape-restricted regressions, where the coefficients are forced to adhere to specific constraints such as monotonicity or curvature, the effectiveness of bootstrap is not proved to be guaranteed.
-In this paper, we will demonstrate the usage of the bootstrap method in shape-restricted regression and proof the effectiveness of bootstrap for constructing pointwise confidence intervals in shape-restricted regression empirically.
+Bootstrap is a powerful and important resampling method for estimating population
+parameters or assessing the accuracy of a statistical procedure by repeatedly 
+sampling the data with replacement. Its effectiveness have been widely recognized
+in linear regression analysis \cite{efron1979bootstrap}, and non-linear regression
+analysis \cite{davidson1999bootstrap}. By bootstrap method, we can estimate the 
+standard errors of the regression coefficients. Even for unknown underlying 
+population distributions, bootstrap method can resample the data with replacement 
+and computes the regression coefficients for each resampled dataset. 
+\cite{hall2013simple}By repeating this process many times, it provides a valid 
+empirical estimate of the standard errors in both linear cases 
+\cite{efron1985bootstrap} and nonlinear cases\cite{wong2019bootstrap}, thus it is
+valuable when the assumptions of traditional standard error estimation techniques 
+are violated. It is also a valid method used to construct confidence intervals for
+regression coefficients. \cite{efron1985bootstrap}By resampling the dataset, 
+bootstrap can determining the percentile intervals of these coefficients, and also
+can obtain approximate confidence intervals for the regression parameters. 
+\cite{cui2012evaluating} Bootstrap can also construct the approximate confidence 
+interval for certain time points f(t)s in the function by simulating f'(t) certain
+times in certain time points. \cite{horowitz2018bootstrap} However, when dealing 
+with shape-restricted regressions, where the coefficients are forced to adhere to 
+specific constraints such as monotonicity or curvature, the effectiveness of 
+bootstrap is not proved to be guaranteed. In this paper, we will demonstrate the
+usage of the bootstrap method in shape-restricted regression and proof the 
+effectiveness of bootstrap for constructing pointwise confidence intervals in 
+shape-restricted regression empirically.
 
 The rest of the paper is organized as the follows. 
-Section~\ref{Bootstrap Method for Constructing Confidence Intervals} gives a review of bootstrap method for constructing confidence intervals.
-Section~\ref{Shape Restricted Example} gives out a shape-restricted regression example and the usage of bootstrap to build the pointwise confidence intervals for certain time points.
-Section~\ref{Simulation Study} shows a simulation study to assess the performance of the methods.
+Section~\ref{Bootstrap Method for Constructing Confidence Intervals}
+gives a review of bootstrap method for constructing confidence intervals. 
+Section~\ref{Shape Restricted Example} gives out a shape-restricted regression
+example and the usage of bootstrap to build the pointwise confidence intervals 
+for certain time points. Section~\ref{Simulation Study} shows a simulation study
+to assess the performance of the methods.
 explores the case where a combination of the first two scenarios occurs. An  
@@
 
-The bootstrap method is a powerful resampling technique used to construct confidence intervals for population parameters or estimates when the underlying distribution is unknown or difficult to determine.
-\cite{hall2013simple}It is useful in regression analysis to estimate the uncertainty associated with the regression coefficients or for certain time points inside the regression function.
-Specifically, the bootstrap method basically contains three steps:
+The bootstrap method is a powerful resampling technique used to construct 
+confidence intervals for population parameters or estimates when the underlying 
+distribution is unknown or difficult to determine. \cite{hall2013simple}It is 
+useful in regression analysis to estimate the uncertainty associated with the 
+regression coefficients or for certain time points inside the regression 
+function. Specifically, the bootstrap method basically contains three steps:
 
 \begin{enumerate}[label=\arabic*.]
-    \item Let \(v\) represent a population parameter of interest (e.g., mean, median, standard deviation, etc.), which is drawn from an unknown population distribution \(F\).
-    \item Generate a bootstrap sample \(x_1, x_2, \ldots, x_n\) from the population, and they are referred to as the original sample dataset.
-    \item Let \(u\) represent a statistic calculated from the bootstrap original sample dataset.
-    \item Using the data in the original sample dataset as the "population," perform nonparametric resampling with replacement to obtain a resampled sample (also known as the Bootstrap sample), denoted as \(x_1^*, x_2^*, \ldots, x_n^*\) (the number of data points in the Bootstrap sample must be the same as the number of data points in the original sample).
-    \item Let \(u^*\) represent the statistic computed by the Bootstrap sample datasets, and this will be the bootstrap estimated statistic for the population statistic.
+    \item Let \(v\) represent a population parameter of interest (e.g., mean,
+    median, standard deviation, etc.), which is drawn from an unknown population
+    distribution \(F\).
+    \item Generate a bootstrap sample \(x_1, x_2, \ldots, x_n\) from the 
+    population, and they are referred to as the original sample dataset.
+    \item Let \(u\) represent a statistic calculated from the bootstrap original
+    sample dataset.
+    \item Using the data in the original sample dataset as the "population," 
+    perform nonparametric resampling with replacement to obtain a resampled sample
+    (also known as the Bootstrap sample), denoted as \(x_1^*, x_2^*, \ldots, x_n^*\)
+    (the number of data points in the Bootstrap sample must be the same as the 
+    number of data points in the original sample).
+    \item Let \(u^*\) represent the statistic computed by the Bootstrap 
+    sample datasets, and this will be the bootstrap estimated statistic 
+    for the population statistic.
 
@@
 
-Bootstrap method has been proved that it is an excellent method to estimate statistic \cite{efron1979bootstrap}, the \(u^*\) we obtained from the resampling dataset is a good estimator for the \(v\) as a population parameter.
-According to the bootstrap method, we can also calculate the confidence interval for the parameters, or the coefficients of a certain regression, or for certain time points in the regression.
-In this article, we will focus on the method of construct a pointwise confidence interval by bootstrap.
-To construct a pointwise confidence interval using the bootstrap method, the procedure involves the following steps:
+Bootstrap method has been proved that it is an excellent method to estimate 
+statistic \cite{efron1979bootstrap}, the \(u^*\) we obtained from the resampling
+dataset is a good estimator for the \(v\) as a population parameter. According 
+to the bootstrap method, we can also calculate the confidence interval for the 
+parameters, or the coefficients of a certain regression, or for certain time points
+in the regression. In this article, we will focus on the method of construct a 
+pointwise confidence interval by bootstrap. To construct a pointwise confidence 
+interval using the bootstrap method, the procedure involves the following steps:
 
 \begin{enumerate}[label=\arabic*.]
-    \item First we observed a specific time point \(t\) that we are interested and its corresponding true value \(f(t)\), and build them as a pair \(t, f(t)\).
-    \item According to the dataset, fit \(\hat{f}\) as the estimated regression for the dataset.
-    \item Generate a bootstrap sample \(x_1, x_2, \ldots, x_n\) from the population by sampling with replacement, and they are referred to as the original sample dataset. 
-    \item Then  \( [\hat{f}_n(t) - \hat{q}_{1-\alpha/2,n-1/3}, \hat{f}_n(t) - \hat{q}_{\alpha/2,n-1/3} ]\)  would be the bootstrap estimated pointwise confidence interval where \(\hat{q}_\alpha\) denoted the \(\alpha\)th quantile of the time point \(t\).
+    \item First we observed a specific time point \(t\) that we are interested 
+    and its corresponding true value \(f(t)\), and build them as a pair \(t, f(t)\).
+    \item According to the dataset, fit \(\hat{f}\) as the estimated regression for
+    the dataset.
+    \item Generate a bootstrap sample \(x_1, x_2, \ldots, x_n\) from the population
+    by sampling with replacement, and they are referred to as the original sample
+    dataset. 
+    \item Then  
+    \( [\hat{f}_n(t) - \hat{q}_{1-\alpha/2,n-1/3}, \hat{f}_n(t) - \hat{q}_{\alpha/2,n-1/3} ]\)
+    would be the bootstrap estimated pointwise confidence interval 
+    where \(\hat{q}_\alpha\) denoted the \(\alpha\)th quantile of the time point \(t\).
 
@@
 
-It has been proved that the bootstrap method can be used as a good estimator for the pointwise confidence interval in linear regressions and non-linear regressions\cite{efron1979bootstrap}\cite{davidson1999bootstrap}, and some examples in certain configurations are given.\cite{ruhe2019bootstrap}\cite{ma2019inference}\cite{dugas2010pointwise} But in certain special cases(i.e.
-shape-restricted splines regressions) there is no certain resource have not prove that it is a good method to build pointwise confidence interval via bootstrap.
+It has been proved that the bootstrap method can be used as a good estimator for
+the pointwise confidence interval in linear regressions and non-linear regressions
+\cite{efron1979bootstrap}\cite{davidson1999bootstrap}, and some examples in certain
+configurations are given.\cite{ruhe2019bootstrap}\cite{ma2019inference}
+\cite{dugas2010pointwise} But in certain special cases(i.e. shape-restricted splines 
+regressions) there is no certain resource have not prove that it is a good method to
+build pointwise confidence interval via bootstrap.
 
-Shape-restricted splines regressions are piecewise polynominal, differentiable to a certain degree and have certain restrictions like monotonicity or convexity.\cite{meyer2008inference} Given these conditions, the application of the bootstrap method to estimate pointwise confidence intervals for specific time points within the regression cannot be guaranteed to be suitable.
-And in the rest of the article we gives out an example of shape-restricted regression and the method to fit confidence interval for certain time points in the function.
+Shape-restricted splines regressions are piecewise polynominal, differentiable to a
+certain degree and have certain restrictions like monotonicity or convexity.
+\cite{meyer2008inference} Given these conditions, the application of the bootstrap
+method to estimate pointwise confidence intervals for specific time points within 
+the regression cannot be guaranteed to be suitable. And in the rest of the article
+we gives out an example of shape-restricted regression and the method to fit confidence
+interval for certain time points in the function.
 
@@
 
-In some situations the regression is forced to be shape-restricted to improve the predictive performance and reduce overfitting if the underlying regression function takes the specific form.
-Some regressions are naturally constrained to convexity or concativity in a lot of disciplines like economics, biology, and psychological studies, and other ares.\cite{jieying2022heteroscedastic} \cite{guntuboyina2018nonparametric} Some popular examples like cost function and profit function in economics\cite{gallant1984imposing}, precipitation data analysis\cite{molitor2002bayesian}.
-In this article we gives out an example of the relationship between income and the age of Canadian workers.
-The data is given from R package SemiPar.
-For those situations, Regression splines are smooth, flexible, and parsimonious nonparametric function estimators, and it offers an effective approach to enhance the inference of shape-restricted regression.
-\cite{meyer2008inference} In this dataset, a nondecreasing relationship between the age of workers and the expected logarithm of the income was considered.
-\cite{wang2021shape}  Splines2 provides implementation of those spline basis functions via R language, and we use that to build a non-decreasing curve by i-spline that force the coefficients to be non-negative with degree of freedom = 6.
-Then, we selected 10 time points, denoted as $t$, with equal intervals from the dataset, corresponding to one of them is the regression time points \(f'(t)\) that fitted by iSpline.
-We also performed bootstrap resampling 1000 times to obtain the 95\% quantile pointwise confidence interval for each points.
-In the figure below, the red line represents the fitted i-spline regression, the yellow line is the smooth regression, and we build ten pointwise confidence intervals for 10 certain time points.
-The result is shown in Figure ~\ref{fig:semipar}.
+In some situations the regression is forced to be shape-restricted to improve
+the predictive performance and reduce overfitting if the underlying regression 
+function takes the specific form. Some regressions are naturally constrained to
+convexity or concativity in a lot of disciplines like economics, biology, and 
+psychological studies, and other ares.\cite{jieying2022heteroscedastic} 
+\cite{guntuboyina2018nonparametric} Some popular examples like cost function and 
+profit function in economics\cite{gallant1984imposing}, precipitation data analysis
+\cite{molitor2002bayesian}. In this article we gives out an example of the 
+relationship between income and the age of Canadian workers. The data is given from
+R package SemiPar. For those situations, Regression splines are smooth, flexible, 
+and parsimonious nonparametric function estimators, and it offers an effective approach
+to enhance the inference of shape-restricted regression. \cite{meyer2008inference} 
+In this dataset, a nondecreasing relationship between the age of workers and the 
+expected logarithm of the income was considered. \cite{wang2021shape}  Splines2 provides
+implementation of those spline basis functions via R language, and we use that to build 
+a non-decreasing curve by i-spline that force the coefficients to be non-negative with
+degree of freedom = 6. Then, we selected 10 time points, denoted as $t$, with equal 
+intervals from the dataset, corresponding to one of them is the regression time points
+\(f'(t)\) that fitted by iSpline. We also performed bootstrap resampling 1000 times to
+obtain the 95\% quantile pointwise confidence interval for each points. In the figure
+below, the red line represents the fitted i-spline regression, the yellow line is the
+smooth regression, and we build ten pointwise confidence intervals for 10 certain time
+points. The result is shown in Figure ~\ref{fig:semipar}.
 
@@
   \includegraphics[width=0.8\textwidth]{SemiparCI.png}
-  \caption{CI build for the shape-restricted regression: The red line is the fitted i-splines regression, the yellow line is the smoothing splines, the grey area represents the \(95\%\) confidence interval for the smoothing splines, and the black solid intervals are the bootstrap pointwise confidence intervals for certain time points.
-}
+  \caption{CI build for the shape-restricted regression: The red line is the 
+  fitted i-splines regression, the yellow line is the smoothing splines, the
+  grey area represents the \(95\%\) confidence interval for the smoothing splines, 
+  and the black solid intervals are the bootstrap pointwise confidence intervals for
+  certain time points. }
   \label{fig:semipar}
@@
 
-We can see that, for this one-time example all the pointwise confidence intervals constructed by the bootstrap method include the fitted regression.
-But it is not a valid proof that bootstrap is a good method for constructing pointwise confidence intervals since the regression is fitted by the dataset, and the criteria is given by \(f'(t)\) which is given by the regression but not the the true value \(f(t)\).
-In this case, a simulation study is required to further prove the effectiveness of bootstrap pointwise confidence intervals.
+We can see that, for this one-time example all the pointwise confidence intervals 
+constructed by the bootstrap method include the fitted regression. But it is not a
+valid proof that bootstrap is a good method for constructing pointwise confidence 
+intervals since the regression is fitted by the dataset, and the criteria is given
+by \(f'(t)\) which is given by the regression but not the the true value \(f(t)\).
+In this case, a simulation study is required to further prove the effectiveness of 
+bootstrap pointwise confidence intervals.
 
@@
 
-Since the underlying distribution is unknown, we need to perform a simulation study to test whether the fitted pointwise confidence interval is accurate for the regression.
+Since the underlying distribution is unknown, we need to perform a simulation
+study to test whether the fitted pointwise confidence interval is accurate 
+for the regression.
 
-We define three functions: \(y = 0.25(x - 0.9)\) , \(y = 0.02(x^3+1.2)\) , and \( y = 0.1 (5\Phi((x - 2) / 0.3) + 1)\) , where \(\Phi\) is the cumulative distribution function of the standard normal distribution.
-For those functions, the validity of the bootstrap method to build the confidence intervals for the coefficients and standard error has already been proved.
-\cite{jieying2022heteroscedastic} And in this article we want to further prove the validity of the bootstrap method to build the pointwise confidence intervals for certain time points in the domain of the function.
-First of all, we randomly generate 1000 points \(x\) in the domain of \([0,30]\), and we calculate its corresponding values \(y(x)\), and make simulation data points \(f'(x)\) by add noise to the true value \(f(x)\).
-The noise is added from a standard normal distribution with \(\mu = 0\) and \(\sigma = \) \(1\).
-And then we make the paired values \((x, y\text{ with noise})\) be the dataset, while we know the true values of \(f(x)\) as well.
+We define three functions: \(y = 0.25(x - 0.9)\) , \(y = 0.02(x^3+1.2)\) , and
+\( y = 0.1 (5\Phi((x - 2) / 0.3) + 1)\) , where \(\Phi\) is the cumulative 
+distribution function of the standard normal distribution. For those functions,
+the validity of the bootstrap method to build the confidence intervals for the
+coefficients and standard error has already been proved. 
+\cite{jieying2022heteroscedastic} And in this article we want to further prove
+the validity of the bootstrap method to build the pointwise confidence intervals
+for certain time points in the domain of the function. First of all, we randomly
+generate 1000 points \(x\) in the domain of \([0,30]\), and we calculate its 
+corresponding values \(y(x)\), and make simulation data points \(f'(x)\) by add 
+noise to the true value \(f(x)\). The noise is added from a standard normal 
+distribution with \(\mu = 0\) and \(\sigma = \) \(1\). And then we make the 
+paired values \((x, y\text{ with noise})\) be the dataset, while we know the 
+true values of \(f(x)\) as well.
 
@@
   \includegraphics[width=0.8\textwidth]{DataAndRegressions.png}
-  \caption{The generated dataset, true functions and fitted i-splines regressions: the shaded green curve represents the true functions, the pink points are the data pair \((x, f'(x))\) where \(f'(x)\) is generated by \(f(x)\) add noise, and the red curves are the fitted i-splines regression curve with degrees of freedom\(= 6,10,15\), from top to bottom}
+  \caption{The generated dataset, true functions and fitted i-splines regressions
+  : the shaded green curve represents the true functions, the pink points are the
+  data pair \((x, f'(x))\) where \(f'(x)\) is generated by \(f(x)\) add noise,
+  and the red curves are the fitted i-splines regression curve with degrees of 
+  freedom\(= 6,10,15\), from top to bottom}
   \label{fig:DataAndRegressions}
@@
 
-We use quadratic i-splines function to enforce the monotonicity of the function and we picked degrees of freedom 6,10,15 to build the regression for the dataset.
-The generated dataset and regressions is shown in Figure ~\ref{fig:DataAndRegressions}.
-In each configuration, we select 1, 5, 10, 15, 20, 25, 30 as the time points from the dataset and perform bootstrap resampling 1000 times to estimate the \(95\%\) quantile pointwise confidence intervals for each of the selected time points.
-We repeat this process 1000 times to see how many times these confidence intervals can contain the true result.
-The results are shown in Table ~\ref{Table}.
+We use quadratic i-splines function to enforce the monotonicity of the function
+and we picked degrees of freedom 6,10,15 to build the regression for the dataset.
+The generated dataset and regressions is shown in Figure 
+~\ref{fig:DataAndRegressions}. In each configuration, we select 1, 5, 10, 15, 20,
+25, 30 as the time points from the dataset and perform bootstrap resampling 1000 
+times to estimate the \(95\%\) quantile pointwise confidence intervals for each 
+of the selected time points. We repeat this process 1000 times to see how many 
+times these confidence intervals can contain the true result. The results are 
+shown in Table ~\ref{Table}.
 
@@
 
-In table ~\ref{Table}, \(x\) represents the certain time point we selected in the domain of the function, and \(f(x)\) is its true value calculated by the certain known function.
-CP represents coverage percentage of pointwise confidence interval we built by the bootstrap methods under certain degrees of freedom.
-We can see that in all those functions and degrees of freedom we have given, the bootstrap method gives pointwise confidence intervals coverage that are closed to the nominal level \(95\%\).
+In table ~\ref{Table}, \(x\) represents the certain time point we 
+selected in the domain of the function, and \(f(x)\) is its true value
+calculated by the certain known function. CP represents coverage
+percentage of pointwise confidence interval we built by the bootstrap 
+methods under certain degrees of freedom. We can see that in all those 
+functions and degrees of freedom we have given, the bootstrap method 
+gives pointwise confidence intervals coverage that are closed to the 
+nominal level \(95\%\).
 
@@
 \label{Conclusion}
-In this study, we explored the application of the bootstrap method of building pointwise confidence intervals in shape-restricted cases.
-We demonstrated its effectiveness in constructing pointwise confidence intervals for certain time points within the regression function.
+In this study, we explored the application of the bootstrap method of 
+building pointwise confidence intervals in shape-restricted cases. 
+We demonstrated its effectiveness in constructing pointwise confidence
+intervals for certain time points within the regression function.
 
-We gives out a simulation study to prove that the pointwise confidence intervals constructed using the bootstrap method provide good empirical coverage for the true values of the regression function.
-This suggests that the bootstrap method is a valid approach for enhancing the inference of shape-restricted regressions, even for pointwise confidence intervals.
+We gives out a simulation study to prove that the pointwise confidence
+intervals constructed using the bootstrap method provide good 
+empirical coverage for the true values of the regression function. 
+This suggests that the bootstrap method is a valid approach for 
+enhancing the inference of shape-restricted regressions, even for 
+pointwise confidence intervals.
 
-Our findings support the utility of the bootstrap method to build the pointwise confidence intervals in cases where regression models have specific constraints such as monotonicity or curvature.
-However, it's important to consider the assumptions and limitations of the bootstrap method and validate its performance for specific datasets and applications.
+Our findings support the utility of the bootstrap method to build
+the pointwise confidence intervals in cases where regression models
+have specific constraints such as monotonicity or curvature. However
+, it's important to consider the assumptions and limitations of the
+bootstrap method and validate its performance for specific datasets and applications.
 

### 2023-08-24 Manuscript/manuscript.tex
Add files via upload

--- 2023-08-14 Manuscript/manuscript.tex
@@
 
-Bootstrap is a powerful and important resampling method for estimating population parameters or assessing the accuracy of a statistical procedure by repeatedly sampling the data with replacement.
-Its effectiveness have been widely recognized in linear regression analysis \cite{efron1979bootstrap}, and non-linear regression analysis \cite{davidson1999bootstrap}.
-By bootstrap method, we can estimate the standard errors of the regression coefficients.
-Even for unknown underlying population distributions, bootstrap method can resample the data with replacement and computes the regression coefficients for each resampled dataset.
-\cite{hall2013simple}By repeating this process many times, it provides a valid empirical estimate of the standard errors in both linear cases \cite{efron1985bootstrap} and nonlinear cases\cite{wong2019bootstrap}, thus it is valuable when the assumptions of traditional standard error estimation techniques are violated.
-It is also a valid method used to construct confidence intervals for regression coefficients.
-\cite{efron1985bootstrap}By resampling the dataset, bootstrap can determining the percentile intervals of these coefficients, and also can obtain approximate confidence intervals for the regression parameters.
-\cite{cui2012evaluating} Bootstrap can also construct the approximate confidence interval for certain time points f(t)s in the function by simulating f'(t) certain times in certain time points.
-\cite{horowitz2018bootstrap} However, when dealing with shape-restricted regressions, where the coefficients are forced to adhere to specific constraints such as monotonicity or curvature, the effectiveness of bootstrap is not proved to be guaranteed.
+In certain area and cases, apply shape restrictions, such as monotonicity or convexity to estimate a certain function is reasonable and not uncommon in many fields.\cite{guo2019smooth} There are several methods to build shape-restricted regressions to do analysis the regressions, like quadratic programming.\cite{meyer2013simple} However, due to shape restrictions, it is not quite accurate to estimate the uncertainty of the parameters with normal methods like MLE (Maximum likelihood estimation) since parameters will sometimes lies on the boundary.
+In this paper, we consider to use bootstrap method to replace MLE method to estimate the uncertainty of the parameters, specifically, of certain time points in the regression curve.
+Although the bootstrap method is a valid method used to construct confidence intervals for regression coefficients, \cite{efron1985bootstrap}and its effectiveness have been widely recognized in linear regression analysis \cite{efron1979bootstrap}, and non-linear regression analysis \cite{davidson1999bootstrap}.
+However, when dealing with shape-restricted regressions, where the coefficients are forced to adhere to specific constraints such as monotonicity or curvature, the effectiveness of bootstrap is not proved to be guaranteed.
 In this paper, we will demonstrate the usage of the bootstrap method in shape-restricted regression and proof the effectiveness of bootstrap for constructing pointwise confidence intervals in shape-restricted regression empirically.
@@
 
-\section{Bootstrap Method for Constructing Confidence Intervals}
+\section{Bootstrap Method review}
 \label{Bootstrap Method for Constructing Confidence Intervals}
 
-The bootstrap method is a powerful resampling technique used to construct confidence intervals for population parameters or estimates when the underlying distribution is unknown or difficult to determine.
-\cite{hall2013simple}It is useful in regression analysis to estimate the uncertainty associated with the regression coefficients or for certain time points inside the regression function.
-Specifically, the bootstrap method basically contains three steps:
+The bootstrap is a powerful and important resampling method for estimating population parameters or assessing the accuracy of a statistical procedure by repeatedly sampling the data with replacement.
+Its effectiveness have been widely recognized in linear regression analysis \cite{efron1979bootstrap}, and non-linear regression analysis \cite{davidson1999bootstrap}.
+By bootstrap method, we can estimate the standard errors and confidence intervals for the regression coefficients.
+Even for unknown underlying population distributions, bootstrap method can resample the data with replacement and computes the regression coefficients for each resampled dataset.
+\cite{hall2013simple}By repeating this process many times, it provides a valid empirical estimate of the standard errors in both linear cases \cite{efron1985bootstrap} and nonlinear cases\cite{wong2019bootstrap}, thus it is valuable when the assumptions of traditional standard error estimation techniques are violated.
+It is also a valid method used to construct confidence intervals for regression coefficients.
+\cite{efron1985bootstrap}By resampling the dataset, bootstrap can determining the percentile intervals of these coefficients, and also can obtain approximate confidence intervals for the regression parameters.
+\cite{cui2012evaluating} Bootstrap can also construct the approximate confidence interval for certain time points f(t)s in the function by simulating f'(t) certain times in certain time points.
+\cite{horowitz2018bootstrap} Thus it is useful in regression analysis to estimate the uncertainty associated with the regression coefficients or for certain time points inside the regression function.
+\cite{Efron2011-sn}For convenience, in here we just talk about simple regression model which only contains one independent variable and one dependent variable.
+Specifically, the bootstrap method basically contains the following steps:
 
 \begin{enumerate}[label=\arabic*.]
-    \item Let \(v\) represent a population parameter of interest (e.g., mean, median, standard deviation, etc.), which is drawn from an unknown population distribution \(F\).
-    \item Generate a bootstrap sample \(x_1, x_2, \ldots, x_n\) from the population, and they are referred to as the original sample dataset.
-    \item Let \(u\) represent a statistic calculated from the bootstrap original sample dataset.
+    \item Suppose we observed specific independent data points \(x_1, x_2, \ldots, x_n\) from a dataset, and for convenience we placed them inside a vector \(X = (x_1, x_2, \ldots, x_n)\), and since we want to construct a regression for the dataset, these data points are supposed to have a corresponding \(y\) values as dependent variable, and this makes the data points becomes pairs as \(X = (x_1,y_1) , (x_2,y_2),  \ldots, (x_n,y_n)\), and we call this as original dataset \(X\).
+Then we use the original dataset \(X)\) to create a simple regression model \(y = \beta_0 + \beta_1 x\).
+    \item From the original dataset \(X\), generate \(n = B\) bootstrap samples, and placed them inside a dataset denoted as \(X^* = x_1^*, x_2^*, \ldots, x_n^*\), each bootstrap samples are obtained by sampling inside the original dataset \(X\) with replacement.
+    \item With this bootstrap dataset, we can do the inference for any statistics we are interested in the original dataset.
+For exsample, if we are interested in the standard error \(s(x)\) for the original dataset, we may use the bootstrap dataset to inference it.
+The bootstrap estimate of standard error is the standard deviation calculated by the bootstrap dataset \(X^*\):
+    \begin{equation}
+      \hat{se_{boot}} = \{\sum_{b=1}^{B}[s(X^*)-s(*)]^2/(B-1)\}^{1/2}
+    \end{equation}
+
     \item Using the data in the original sample dataset as the "population," perform nonparametric resampling with replacement to obtain a resampled sample (also known as the Bootstrap sample), denoted as \(x_1^*, x_2^*, \ldots, x_n^*\) (the number of data points in the Bootstrap sample must be the same as the number of data points in the original sample).
-    \item Let \(u^*\) represent the statistic computed by the Bootstrap sample datasets, and this will be the bootstrap estimated statistic for the population statistic.
+    \item If we are interested in confidence interval for certain regression coefficients or time points, we can also use bootstrap method to construct it, in this situation, \( [\hat{f}_n(t) - \hat{q}_{1-\alpha/2,n-1/3}, \hat{f}_n(t) - \hat{q}_{\alpha/2,n-1/3} ]\)  would be the bootstrap estimated pointwise confidence interval where \(\hat{q}_\alpha\) denoted the \(\alpha\)th quantile of the time point \(t\).
 
@@
 In this article, we will focus on the method of construct a pointwise confidence interval by bootstrap.
-To construct a pointwise confidence interval using the bootstrap method, the procedure involves the following steps:
-
-\begin{enumerate}[label=\arabic*.]
-    \item First we observed a specific time point \(t\) that we are interested and its corresponding true value \(f(t)\), and build them as a pair \(t, f(t)\).
-    \item According to the dataset, fit \(\hat{f}\) as the estimated regression for the dataset.
-    \item Generate a bootstrap sample \(x_1, x_2, \ldots, x_n\) from the population by sampling with replacement, and they are referred to as the original sample dataset. 
-    \item Then  \( [\hat{f}_n(t) - \hat{q}_{1-\alpha/2,n-1/3}, \hat{f}_n(t) - \hat{q}_{\alpha/2,n-1/3} ]\)  would be the bootstrap estimated pointwise confidence interval where \(\hat{q}_\alpha\) denoted the \(\alpha\)th quantile of the time point \(t\).
-
-\end{enumerate}
-
 It has been proved that the bootstrap method can be used as a good estimator for the pointwise confidence interval in linear regressions and non-linear regressions\cite{efron1979bootstrap}\cite{davidson1999bootstrap}, and some examples in certain configurations are given.\cite{ruhe2019bootstrap}\cite{ma2019inference}\cite{dugas2010pointwise} But in certain special cases(i.e.
@@
 
-We define three functions: \(y = 0.25(x - 0.9)\) , \(y = 0.02(x^3+1.2)\) , and \( y = 0.1 (5\Phi((x - 2) / 0.3) + 1)\) , where \(\Phi\) is the cumulative distribution function of the standard normal distribution.
+We define three functions: \(y = 0.25(x - 0.9)\) , \(y = 0.02(x^3+1.2)\) , and \(y = 0.1(5\Phi((x - 2)/0.3) + 1)\) , where \(\Phi\) is the cumulative distribution function of the standard normal distribution.
 For those functions, the validity of the bootstrap method to build the confidence intervals for the coefficients and standard error has already been proved.
 \cite{jieying2022heteroscedastic} And in this article we want to further prove the validity of the bootstrap method to build the pointwise confidence intervals for certain time points in the domain of the function.
-First of all, we randomly generate 1000 points \(x\) in the domain of \([0,30]\), and we calculate its corresponding values \(y(x)\), and make simulation data points \(f'(x)\) by add noise to the true value \(f(x)\).
+First of all, we randomly generate some data points \(x\) in the domain of \([0,4]\), and we calculate its corresponding values \(y(x)\), and make simulation data points \(f'(x)\) by add noise to the true value \(f(x)\).
 The noise is added from a standard normal distribution with \(\mu = 0\) and \(\sigma = \) \(1\).
@@
   \centering
-  \includegraphics[width=0.8\textwidth]{DataAndRegressions.png}
-  \caption{The generated dataset, true functions and fitted i-splines regressions: the shaded green curve represents the true functions, the pink points are the data pair \((x, f'(x))\) where \(f'(x)\) is generated by \(f(x)\) add noise, and the red curves are the fitted i-splines regression curve with degrees of freedom\(= 6,10,15\), from top to bottom}
+  \includegraphics[width=0.8\textwidth]{DataPointsGeneration.png}
+  \caption{The generated dataset while n=100, true functions and fitted i-splines regressions: the shaded green curve represents the true functions, the pink points are the data pair \((x, f'(x))\) where \(f'(x)\) is generated by \(f(x)\) add noise, and the red curves are the fitted i-splines regression curve with degrees of freedom\(= 6,10,15\), from top to bottom}
   \label{fig:DataAndRegressions}
@@
 
-We use quadratic i-splines function to enforce the monotonicity of the function and we picked degrees of freedom 6,10,15 to build the regression for the dataset.
+We use quadratic i-splines function to enforce the monotonicity of the function and we picked degrees of freedom 6 and 10 to build the regression for the dataset.
 The generated dataset and regressions is shown in Figure ~\ref{fig:DataAndRegressions}.
-In each configuration, we select 1, 5, 10, 15, 20, 25, 30 as the time points from the dataset and perform bootstrap resampling 1000 times to estimate the \(95\%\) quantile pointwise confidence intervals for each of the selected time points.
+While according to the law of large number, we also expect that the result will be closer to \(95\%\) while n gets larger, so we also did a simulation for \(n = 1000\) to see the numeric coverage percentiles.
+In each configuration, we select \(0.5,1,1.5,2,2.5,3,3.5,4\) as the time points from the dataset and perform bootstrap resampling 1000 times to estimate the \(95\%\) quantile pointwise confidence intervals for each of the selected time points.
 We repeat this process 1000 times to see how many times these confidence intervals can contain the true result.
-The results are shown in Table ~\ref{Table}.
+The results are shown in Table ~\ref{Table} and Table ~/ref{2}.
 
@@
   \centering
-  \label{Table}
-  \caption{Results of functions for different degrees of freedom}
-  \begin{tabular}{|c|c|c|c|c|}
+  \caption{Results for Different Degrees of Freedom (\(n = 100\))}
+  \label{Table1}
+  \begin{tabular}{|c|c|c|c|}
     \hline
-    \textbf{x} & \textbf{f(x)} & \textbf{CP of df\_6} & \textbf{CP of df\_10} & \textbf{CP of df\_15} \\
+    \textbf{x} & \textbf{Function} & \textbf{CP of df\_6} & \textbf{CP of df\_10} \\
     \hline
-    \multicolumn{5}{|c|}{\(y = 0.25(x - 0.9)\)} \\
+    \multicolumn{4}{|c|}{\(y = 0.25(x - 0.9)\)} \\
     \hline
-    1 & 0.025 & 0.936 & 0.944 & 0.939 \\
+    0.5 & -0.100 & 0.952 & 0.959 \\
     \hline
-    5 & 1.025 & 0.960 & 0.958 & 0.948 \\
+    1.0 & 0.025 & 0.956 & 0.948 \\
     \hline
-    10 & 2.275 & 0.956 & 0.950 & 0.951 \\
+    1.5 & 0.150 & 0.959 & 0.940\\
     \hline
-    15 & 3.525 & 0.959 & 0.954 & 0.954 \\
+    2.0 & 0.275 & 0.956 & 0.953 \\
     \hline
-    20 & 4.775 & 0.941 & 0.949 & 0.961 \\
+    2.5 & 0.400 & 0.952 & 0.957 \\
     \hline
-    25 & 6.025 & 0.953 & 0.946 & 0.942 \\
+    3.0 & 0.525 & 0.950 & 0.953 \\
     \hline
-    30 & 7.275 & 0.919 & 0.955 & 0.947 \\
+    3.5 & 0.650 & 0.945 & 0.950 \\
     \hline
-    \multicolumn{5}{|c|}{\(y = 0.02(x^3+1.2)\)} \\
+    4.0 & 0.775 & 0.926 & 0.908 \\
     \hline
-    1 & 0.025 & 0.893 & 0.940 & 0.959 \\
+    \multicolumn{4}{|c|}{\(y = 0.02(x^3+1.2)\)} \\
     \hline
-    5 & 1.025 & 0.932 & 0.948 & 0.958 \\
+    0.5 & 0.027 & 0.938 & 0.937 \\
     \hline
-    10 & 2.275 & 0.937 & 0.948 & 0.941 \\
+    1.0 & 0.044 & 0.946 & 0.952 \\
     \hline
-    15 & 3.525 & 0.942 & 0.951 & 0.953 \\
+    1.5 & 0.092 & 0.932 & 0.943 \\
     \hline
-    20 & 4.775 & 0.939 & 0.951 & 0.957 \\
+    2.0 & 0.184 & 0.936 & 0.945 \\
     \hline
-    25 & 6.025 & 0.952 & 0.959 & 0.963 \\
+    2.5 & 0.337 & 0.942 & 0.948 \\
     \hline
-    30 & 7.275 & 0.947 & 0.943 & 0.943 \\
+    3.0 & 0.564 & 0.960 & 0.946 \\
     \hline
-    \multicolumn{5}{|c|}{\(y = 0.1 (5\Phi((x - 2) / 0.3) + 1)\)} \\
+    3.5 & 0.882 & 0.940 & 0.943 \\
     \hline
-    1 & 0.025 & 0.686 & 0.847 & 0.901 \\
+    4.0 & 1.304 & 0.907 & 0.907 \\
     \hline
-    5 & 1.025 & 0.279 & 0.800 & 0.852 \\
+    \multicolumn{4}{|c|}{\(y = 0.1 (5\Phi((x - 2) / 0.3) + 1)\)} \\
     \hline
-    10 & 2.275 & 0.947 & 0.937 & 0.942 \\
+    0.5 & 0.100 & 0.938 & 0.947 \\
     \hline
-    15 & 3.525 & 0.937 & 0.953 & 0.961 \\
+    1.0 & 0.100 & 0.927 & 0.941 \\
     \hline
-    20 & 4.775 & 0.929 & 0.950 & 0.957 \\
+    1.5 & 0.124 & 0.826 & 0.830 \\
     \hline
-    25 & 6.025 & 0.953 & 0.924 & 0.922 \\
+    2.0 & 0.350 & 0.962 & 0.958 \\
     \hline
-    30 & 7.275 & 0.919 & 0.858 & 0.832 \\
+    2.5 & 0.576 & 0.835 & 0.816 \\
+    \hline
+    3.0 & 0.600 & 0.935 & 0.945 \\
+    \hline
+    3.5 & 0.600 & 0.957 & 0.953 \\
+    \hline
+    4.0 & 0.600 & 0.875 & 0.840 \\
     \hline
@@
 
-In table ~\ref{Table}, \(x\) represents the certain time point we selected in the domain of the function, and \(f(x)\) is its true value calculated by the certain known function.
+\begin{table}[ht]
+  \centering
+  \caption{Results for Different Degrees of Freedom (\(n = 1000\))}
+  \label{Table2}
+  \begin{tabular}{|c|c|c|c|}
+    \hline
+    \textbf{x} & \textbf{Function} & \textbf{CP of df\_6} & \textbf{CP of df\_10} \\
+    \hline
+    \multicolumn{4}{|c|}{\(y = 0.25(x - 0.9)\)} \\
+    \hline
+    0.5 & -0.100 & 0.956 & 0.948 \\
+    \hline
+    1.0 & 0.025 & 0.953 & 0.957 \\
+    \hline
+    1.5 & 0.150 & 0.961 & 0.955 \\
+    \hline
+    2.0 & 0.275 & 0.967 & 0.955 \\
+    \hline
+    2.5 & 0.400 & 0.956 & 0.953 \\
+    \hline
+    3.0 & 0.525 & 0.949 & 0.961 \\
+    \hline
+    3.5 & 0.650 & 0.952 & 0.946 \\
+    \hline
+    4.0 & 0.775 & 0.952 & 0.937 \\
+    \hline
+    \multicolumn{4}{|c|}{\(y = 0.02(x^3+1.2)\)} \\
+    \hline
+    0.5 & 0.027 & 0.964 & 0.961 \\
+    \hline
+    1.0 & 0.044 & 0.950 & 0.954 \\
+    \hline
+    1.5 & 0.092 & 0.937 & 0.939 \\
+    \hline
+    2.0 & 0.184 & 0.939 & 0.949 \\
+    \hline
+    2.5 & 0.337 & 0.947 & 0.952 \\
+    \hline
+    3.0 & 0.564 & 0.952 & 0.946 \\
+    \hline
+    3.5 & 0.882 & 0.961 & 0.950 \\
+    \hline
+    4.0 & 1.30 & 0.963 & 0.936 \\
+    \hline
+    \multicolumn{4}{|c|}{\(y = 0.1 (5\Phi((x - 2) / 0.3) + 1)\)} \\
+    \hline
+    0.5 & 0.100 & 0.956 & 0.934 \\
+    \hline
+    1.0 & 0.100 & 0.936 & 0.912 \\
+    \hline
+    1.5 & 0.124 & 0.956 & 0.373 \\
+    \hline
+    2.0 & 0.350 & 0.967 & 0.951 \\
+    \hline
+    2.5 & 0.576 & 0.956 & 0.411 \\
+    \hline
+    3.0 & 0.600 & 0.954 & 0.905 \\
+    \hline
+    3.5 & 0.600 & 0.951 & 0.922 \\
+    \hline
+    4.0 & 0.600 & 0.946 & 0.837 \\
+    \hline
+  \end{tabular}
+\end{table}
+
+In table ~\ref{Table1}, \(x\) represents the certain time point we selected in the domain of the function, and \(f(x)\) is its true value calculated by the certain known function.
 CP represents coverage percentage of pointwise confidence interval we built by the bootstrap methods under certain degrees of freedom.
 We can see that in all those functions and degrees of freedom we have given, the bootstrap method gives pointwise confidence intervals coverage that are closed to the nominal level \(95\%\).
+And we can also see that while n gets larger, the result of \(n = 1000\), which can be seen in Table ~\ref{Table2} is much better than \(n = 100\) in each same level of degrees of freedom.
+While degrees of freedom is also an important variable inside the study and we can see that for the different degrees of freedom the result of CP is different either, but since it is not the main scope of this paper, we will not concern a lot about how to choose the best model to enhence the CP result.
 

### 2023-09-11 Manuscript/manuscript.tex
Add files via upload

@@
 
-In certain area and cases, apply shape restrictions, such as monotonicity or convexity to estimate a certain function is reasonable and not uncommon in many fields.\cite{guo2019smooth} There are several methods to build shape-restricted regressions to do analysis the regressions, like quadratic programming.\cite{meyer2013simple} However, due to shape restrictions, it is not quite accurate to estimate the uncertainty of the parameters with normal methods like MLE (Maximum likelihood estimation) since parameters will sometimes lies on the boundary.
-In this paper, we consider to use bootstrap method to replace MLE method to estimate the uncertainty of the parameters, specifically, of certain time points in the regression curve.
+In certain area and cases, apply shape restrictions, such as monotonicity or convexity to estimate a certain function is reasonable and not uncommon in many fields.\cite{guo2019smooth} There are a lot of important applications that includes shape-restricted regressions in various fields.
+Guntuboyina and Sen gives a great summary of the usage of shape-restricted regressions and how those restrictions(like convexity and concativity) arises in different fields.\cite{guntuboyina2018nonparametric} There are several methods to estimate the shape-restricted regressions and build the model for inference like quadratic programming.\cite{meyer2013simple} However, since the parameters of such curves are depends on degrees of freedom, we are more interested in analysis the uncertainty of the curve itself.
+Due to shape restrictions, when we want to estimate the uncertainty of the curve,it is not quite accurate to estimate it with normal methods like MLE (Maximum likelihood estimation) since parameters will sometimes lies on the boundary.
+In this paper, we consider to use the bootstrap method to replace MLE method to estimate the uncertainty of the curve.
+Since the parameters of such curves are depends on degrees of freedom, we are more interested in analysis the uncertainty of the curve itself, specifically, of certain time points inside the regression curve.
 Although the bootstrap method is a valid method used to construct confidence intervals for regression coefficients, \cite{efron1985bootstrap}and its effectiveness have been widely recognized in linear regression analysis \cite{efron1979bootstrap}, and non-linear regression analysis \cite{davidson1999bootstrap}.
@@
 Section~\ref{Bootstrap Method for Constructing Confidence Intervals} gives a review of bootstrap method for constructing confidence intervals.
-Section~\ref{Shape Restricted Example} gives out a shape-restricted regression example and the usage of bootstrap to build the pointwise confidence intervals for certain time points.
-Section~\ref{Simulation Study} shows a simulation study to assess the performance of the methods.
-explores the case where a combination of the first two scenarios occurs. An  
+Section~\ref{Simulation Study} shows a simulation study to assess the performance of the bootstrap method in shape-restricted cases.
+And Section~\ref{Real Data Analysis} gives out a shape-restricted regression example based on a real dataset and the use the bootstrap method to build the pointwise confidence intervals for certain time points and access the method.
+An
 adjusted bootstrap procedure is proposed as a working solution in this case.  
@@
 
-Shape-restricted splines regressions are piecewise polynominal, differentiable to a certain degree and have certain restrictions like monotonicity or convexity.\cite{meyer2008inference} Given these conditions, the application of the bootstrap method to estimate pointwise confidence intervals for specific time points within the regression cannot be guaranteed to be suitable.
-And in the rest of the article we gives out an example of shape-restricted regression and the method to fit confidence interval for certain time points in the function.
-
-\section{Shape Restricted Example}
-\label{Shape Restricted Example}
-
 In some situations the regression is forced to be shape-restricted to improve the predictive performance and reduce overfitting if the underlying regression function takes the specific form.
 Some regressions are naturally constrained to convexity or concativity in a lot of disciplines like economics, biology, and psychological studies, and other ares.\cite{jieying2022heteroscedastic} \cite{guntuboyina2018nonparametric} Some popular examples like cost function and profit function in economics\cite{gallant1984imposing}, precipitation data analysis\cite{molitor2002bayesian}.
-In this article we gives out an example of the relationship between income and the age of Canadian workers.
-The data is given from R package SemiPar.
-For those situations, Regression splines are smooth, flexible, and parsimonious nonparametric function estimators, and it offers an effective approach to enhance the inference of shape-restricted regression.
-\cite{meyer2008inference} In this dataset, a nondecreasing relationship between the age of workers and the expected logarithm of the income was considered.
-\cite{wang2021shape}  Splines2 provides implementation of those spline basis functions via R language, and we use that to build a non-decreasing curve by i-spline that force the coefficients to be non-negative with degree of freedom = 6.
-Then, we selected 10 time points, denoted as $t$, with equal intervals from the dataset, corresponding to one of them is the regression time points \(f'(t)\) that fitted by iSpline.
-We also performed bootstrap resampling 1000 times to obtain the 95\% quantile pointwise confidence interval for each points.
-In the figure below, the red line represents the fitted i-spline regression, the yellow line is the smooth regression, and we build ten pointwise confidence intervals for 10 certain time points.
-The result is shown in Figure ~\ref{fig:semipar}.
 
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=0.8\textwidth]{SemiparCI.png}
-  \caption{CI build for the shape-restricted regression: The red line is the fitted i-splines regression, the yellow line is the smoothing splines, the grey area represents the \(95\%\) confidence interval for the smoothing splines, and the black solid intervals are the bootstrap pointwise confidence intervals for certain time points.
-}
-  \label{fig:semipar}
-\end{figure}
-
-We can see that, for this one-time example all the pointwise confidence intervals constructed by the bootstrap method include the fitted regression.
-But it is not a valid proof that bootstrap is a good method for constructing pointwise confidence intervals since the regression is fitted by the dataset, and the criteria is given by \(f'(t)\) which is given by the regression but not the the true value \(f(t)\).
-In this case, a simulation study is required to further prove the effectiveness of bootstrap pointwise confidence intervals.
+Shape-restricted splines regressions are piecewise polynominal, differentiable to a certain degree and have certain restrictions like monotonicity or convexity.\cite{meyer2008inference} Given these conditions, the application of the bootstrap method to estimate pointwise confidence intervals for specific time points within the regression cannot be guaranteed to be suitable.
+So in this article, we are going to give out a simulation study to test the accessibility and accuracy of the bootstrap method for shape-restricted regression situations.
 
@@
 
-Since the underlying distribution is unknown, we need to perform a simulation study to test whether the fitted pointwise confidence interval is accurate for the regression.
+Since in the shape-restricted cases the underlying distribution is unknown, we want to perform a simulation study to test whether the fitted pointwise confidence interval is accurate for the shape- restricted regressions.
 
-We define three functions: \(y = 0.25(x - 0.9)\) , \(y = 0.02(x^3+1.2)\) , and \(y = 0.1(5\Phi((x - 2)/0.3) + 1)\) , where \(\Phi\) is the cumulative distribution function of the standard normal distribution.
+To do this, We define three functions: \(y = 0.25(x - 0.9)\) , \(y = 0.02(x^3+1.2)\) , and \(y = 0.1(5\Phi((x - 2)/0.3) + 1)\) , where \(\Phi\) is the cumulative distribution function of the standard normal distribution.
 For those functions, the validity of the bootstrap method to build the confidence intervals for the coefficients and standard error has already been proved.
@@
   \centering
-  \includegraphics[width=0.8\textwidth]{DataPointsGeneration.png}
-  \caption{The generated dataset while n=100, true functions and fitted i-splines regressions: the shaded green curve represents the true functions, the pink points are the data pair \((x, f'(x))\) where \(f'(x)\) is generated by \(f(x)\) add noise, and the red curves are the fitted i-splines regression curve with degrees of freedom\(= 6,10,15\), from top to bottom}
+  \includegraphics[width=0.8\textwidth]{Regression.jpg}
+  \caption{The generated dataset while n=100, true functions and fitted i-splines regressions: the shaded green curve represents the true functions, the pink points are the data pair \((x, f'(x))\) where \(f'(x)\) is generated by \(f(x)\) add noise, and the red curves are the fitted i-splines regression curve with degrees of freedom\(= 6, 10\), from top to bottom}
   \label{fig:DataAndRegressions}
@@
 We repeat this process 1000 times to see how many times these confidence intervals can contain the true result.
-The results are shown in Table ~\ref{Table} and Table ~/ref{2}.
+The results are shown in Table ~\ref{Table1} and Table ~\ref{Table2}.
 
@@
 And we can also see that while n gets larger, the result of \(n = 1000\), which can be seen in Table ~\ref{Table2} is much better than \(n = 100\) in each same level of degrees of freedom.
-While degrees of freedom is also an important variable inside the study and we can see that for the different degrees of freedom the result of CP is different either, but since it is not the main scope of this paper, we will not concern a lot about how to choose the best model to enhence the CP result.
+We can also see that in some situations, for example, when df = 10, some empirical coverage rate is as low as 0.3 to 0.4, this may due to the degrees of freedom is not suitable for this data regression, which might cause some problems.
+We can also see that via Figure ~\ref{Figure1} when degrees of freedom equals to 10, the curve is not that smooth compare to the curve of degrees of freedom 6, and in some situations, its shape is not even closed to the true function.
+So we can see that degree of freedom is a crucial variable and different degrees of freedom will impact the result of CP of the confidence interval.
+It should be cautious to choose when we are using the splines regression since it will influence the result of the inference a lot.
+However, since it is not the main scope of this paper, we will not concern a lot about how to choose the best model to enhence the CP result.
+Overall, we can see that those pointwise confidence intervals made by bootstrap method works fine in suitable degrees of freedom, and in the rest of this article we will use a real world shape-restricted data to give out an data analysis with the bootstrap method.
+
+\section{Real Data Analysis}
+\label{Real Data Analysis}
+
+ In this part we gives out an example of the relationship between income and the age of Canadian workers.
+The data is given from R package SemiPar.
+For those situations, Regression splines are smooth, flexible, and parsimonious nonparametric function estimators, and it offers an effective approach to enhance the inference of shape-restricted regression.
+\cite{meyer2008inference} In this dataset, a nondecreasing relationship between the age of workers and the expected logarithm of the income was considered.
+\cite{wang2021shape}  Splines2 provides implementation of those spline basis functions via R language, and we use that to build a non-decreasing curve by i-spline that force the coefficients to be non-negative with degree of freedom = 6.
+Then, we selected 10 time points, denoted as $t$, with equal intervals from the dataset, corresponding to one of them is the regression time points \(f'(t)\) that fitted by iSpline.
+We also performed bootstrap resampling 1000 times to obtain the 95\% quantile pointwise confidence interval for each points.
+In the figure below, the red line represents the fitted i-spline regression, the yellow line is the smooth regression, and we build ten pointwise confidence intervals for 10 certain time points.
+The result is shown in Figure ~\ref{fig:semipar}.
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=0.8\textwidth]{SemiparCI.png}
+  \caption{CI build for the shape-restricted regression: The red line is the fitted i-splines regression, the yellow line is the smoothing splines, the grey area represents the \(95\%\) confidence interval for the smoothing splines, and the black solid intervals are the bootstrap pointwise confidence intervals for certain time points.
+}
+  \label{fig:semipar}
+\end{figure}
+
+We can see that, for this one-time example all the pointwise confidence intervals constructed by the bootstrap method include the fitted regression.
+But it is not a valid proof that bootstrap is a good method for constructing pointwise confidence intervals since the regression is fitted by the dataset, and the criteria is given by \(f'(t)\) which is given by the regression but not the the true value \(f(t)\).
+In this case, a simulation study is required to further prove the effectiveness of bootstrap pointwise confidence intervals.
 

### 2023-09-11 Manuscript/manuscript.tex
Add files via upload

@@
 We can also see that in some situations, for example, when df = 10, some empirical coverage rate is as low as 0.3 to 0.4, this may due to the degrees of freedom is not suitable for this data regression, which might cause some problems.
-We can also see that via Figure ~\ref{Figure1} when degrees of freedom equals to 10, the curve is not that smooth compare to the curve of degrees of freedom 6, and in some situations, its shape is not even closed to the true function.
+We can also see that via Figure ~\ref{fig:DataAndRegressions} when degrees of freedom equals to 10, the curve is not that smooth compare to the curve of degrees of freedom 6, and in some situations, its shape is not even closed to the true function.
 So we can see that degree of freedom is a crucial variable and different degrees of freedom will impact the result of CP of the confidence interval.
 It should be cautious to choose when we are using the splines regression since it will influence the result of the inference a lot.
-However, since it is not the main scope of this paper, we will not concern a lot about how to choose the best model to enhence the CP result.
+However, since it is not the main scope of this paper, we will not concern a lot about how to choose the best model to enhance the CP result.
 Overall, we can see that those pointwise confidence intervals made by bootstrap method works fine in suitable degrees of freedom, and in the rest of this article we will use a real world shape-restricted data to give out an data analysis with the bootstrap method.
